### 2019-08-23 sample-sigchi.tex
update

%%
%% This is file `sample-sigchi.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigchi')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigchi.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigchi]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-9999-9/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Andrea Graziani}
\email{andrea.graziani93@outlook.it}
\affiliation{%
  \institution{Università Degli Studi di Roma Tor Vergata}
  \city{Rome}
  \state{Italy}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
MapReduce is often used to run critical jobs such as scientific data analysis. However, evidence in the literature shows that arbitrary faults do occur and can probably corrupt the results of MapReduce jobs; Moreover, ignoring data locality during task scheduling can lead to performance degradation and a pointless bigger network traffic.

We present an original MapReduce algorithm capable to tolerate arbitrary or Byzantine faults experienced by worker nodes and to resolve master node single point of failure problem; moreover, recognizing input data network locations and sizes, our algorithm performs a locality aware task scheduling, improving performance and diminishing network traffic.

Although the execution of a job with our algorithms uses more resources respect to other implementations, like Hadoop, we believe that this cost is acceptable for critical applications that require that level of fault tolerance.

\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigchi]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for all short- and
full-length articles, and optional for two-page abstracts.

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{The 1907 Franklin Model D roadster.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
  doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigchi.tex'.

### 2019-08-23 sample-sigchi.tex
update

@@
 \section{Introduction}
+
+dasdas\footnote{dsadsadsadasdasdasda} fds \cite{Abril07}
+
 ACM's consolidated article template, introduced in 2017, provides a

### 2019-08-23 sample-sigchi.tex
update

--- 2019-08-23 sample-sigchi.tex
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+An important goal in distributed-systems design is to construct a system in such a way it can provide its services even in the presence of faults. In other words, whenever a failure
+occurs, the system should continue to operate in an acceptable way; that is a distributed system is expected to be \textit{fault tolerant}.
+As known, many fault types exists in literature, the most serious of which are \textit{arbitrary failures}, also known as \textit{Byzantine failures}; whenever a that type of fault occurs, a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+In this paper we present an Arbitrary Fault-Tolerant (AFT) MapReduce runtime system.
+
+The key technique used to manage faults is, as , to use redundancy.The key approach to tolerating a faulty process is to organize several identical processes into a group.
+
+ Our BFT
+MapReduce follows the approach of executing each task more
+than once, similarly to the works mentioned above. The chal-
+
+Process groups are part of the solution for building fault-tolerant systems.
+In particular, having a group of identical processes allows us to mask one
+or more faulty processes in that group. In other words, we can replicate
+processes and organize them into a group to replace a single (vulnerable)
+process with a (fault tolerant) group.
+
+An important issue with using process groups to tolerate faults is how
+much replication is needed. To simplify our discussion, let us consider
+only replicated-write systems. A system is said to be k-fault tolerant if it
+can survive faults in k components and still meet its specifications. If the
+components, say processes, fail silently, then having k + 1 of them is enough
+to provide k-fault tolerance. If k of them simply stop, then the answer from
+the other one can be used.
+
+On the other hand, if processes exhibit arbitrary failures, continuing to
+run when faulty and sending out erroneous or random replies, a minimum
+of 2k + 1 processes are needed to achieve k-fault tolerance. In the worst case,
+the k failing processes could accidentally (or even intentionally) generate the
+same reply. However, the remaining k + 1 will also produce the same answer,
+so the client or voter can just believe the majority.
 
 \section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
+\subsection{System Architecture}
+
+Our system is composed by a set of distributed processes:
+
+\begin{description}
+\item[Client Process] the clients that request the execution of jobs composed by map and reduce tasks
+
+\item[Leader Primary Process] It manages the execution of word-count jobs received from clients coordinating Worker Nodes
+
+\item[Backup Primary Process] It manages the execution of word-count jobs received from clients coordinating Worker Nodes
+
+\item[Worker Process] A Worker Process executes map and reduce task
+
+\item[Worker Group] All system's nodes in which worker process are running are logically split into several \textit{Groups}, that is sets of equal worker processes, each of which execute the same commands using same input data in the same order.
+In a group all worker processes run independently on different host and they do not interact with each other in any way.
+Current Leader Primary Process can interact with groups members using a push-based approach in order to schedule map or reduce tasks.
+Although, for performance reasons, not always happen, when a task is sent to the group itself, all members of the group receive it.
+
+The key property that all groups have is that when a
+message is sent to the group itself, all members of the group receive it.
+
+ primary coordinates all write
+operations
+
+ In other words, we can replicate processes and organize them into a group to replace a single (vulnerable) process with a (fault tolerant) group.
+
+ When a task is  for work is generated, either
+by an external client or by one of the workers, it is sent to the coordinator.
+
+as  a set of Task- Trackers that execute tasks
+\end{description}
+
+We assume that clients are always correct, because if they are not there is no point in worrying about the correctness of the job’s output.
+
+The host where current master process is running may fail, for example by crashing or by losing network connectivity.
+Therefore, to ensure system availability in such a way that it can keep on providing its services, multiple master process copies of run on different host, and that a backup copy is promoted to become the new leader when the previous leader fails.
+
+In order to decide when the current leader master process has failed and to elect a new leader, we have used a coordination service like Apache ZooKeeper.
+
+The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover.
+This helps the Mesos master scale to large clusters with many tasks and frameworks.
+A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.
+
+ Mesos consists of a master daemon that manages agent daemons running on each cluster node, and Mesos frameworks that run tasks on these agents.
+
+The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover.
+This helps the Mesos master scale to large clusters with many tasks and frameworks.
+A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.
+
+System model. The system is composed by a set of dis-
+tributed processes: the clients that request the execution of
+jobs composed by map and reduce tasks, the JobTracker that
+manages the execution of a job as explained, a set of Task-
+Trackers that execute tasks, the NameNode that manages ac-
+cess to data stored in HDFS, and a set of DataNodes where
+HDFS stores file blocks. We say that a process is correct if
+it follows the algorithm, otherwise we say it is faulty. We
+also use these two words to denominate a task (map or re-
+duce) that, respectively, returns the result that corresponds to
+an execution in a correct TaskTracker (correct) or not (faulty).
+Processes run in servers in a datacenter.
 

### 2019-08-26 sample-sigchi.tex
up

@@
 
-\item[Worker Process] A Worker Process executes map and reduce task
+\item[Worker Process] A Worker Process executes map and reduce task scheduleted by current Leader Primary Process.
+In order to achieve fault tolerance, any Worker Process must be run indepently on different host.
+In our implementation, each process run on independent Amazon EC2 server
 
@@
 Processes run in servers in a datacenter.
+
+\subsection{The algorithm}
+
+In order to achieve 
+A simplistic solution to make MapReduce
+Byzantine fault-tolerant given the system model would be the
+following. First, the JobTracker starts 2f + 1 replicas of each
+map task in different servers and TaskTrackers. Second, the
+JobTracker starts also 2f + 1 replicas of each reduce task.
+Each reduce task fetches the output from all map replicas,
+picks the most voted results, processes them and stores its
+output in HDFS. In the end, either the client or a special task
+must make the vote of the outputs to pick the most voted. An
+even more simplistic solution would be to run a consensus,
+or Byzantine agreement between each set of map task repli-
+cas and reduce task replicas. This would involve even more
+replicas (typically 3f + 1) and more messages exchanged.
 

### 2019-08-26 sample-sigchi.tex
update

@@
 replicas (typically 3f + 1) and more messages exchanged.
+
+\subsection{Crash failure detection} Workers nodes crash faults are detected using ZooKeeper's coordination service.
+As known, ZooKeeper allows users to store persistently coordination data into several hierarchically grouped nodes, called \textit{znode}.
+However, ZooKeeper has the notion of \textit{ephemeral nodes} too; these special znodes exists as long as the session that created the znode is active, that is when the session ends the znode is deleted.
+A ZooKeeper client establishes a session with the ZooKeeper service
+
+At session expiration the cluster will delete any/all ephemeral nodes owned by that session and immediately notify any/all connected clients of the change
+
+In this way, is very easy to keep check the status of worker nodes by current primary process.
+If any of worker node crash, ZooKeeper automatically delete znode associated to crashed server and notifies current leader.
+
+\subsection{Deferred execution} As known, arbitrary faults are very hard to detect and manage
+
+Deferred execution. Crash faults are detected by the previ-
+ously existing Hadoop mechanisms, and arbitrary faults are
+uncommon, so there is no point in always executing $2f + 1$ replicas to usually obtain the same result.
+
+By default, current leader primary process starts only $f + 1$ replicas of the same task, then wait results checking if they all return the same result.
+If a timeout elapses, or some returned results do not match, more replicas (up to $f$) are started, until there are $f + 1$ matching replies.
+
+In the best case, without Byzantine faults, only f + 1 replicas are started. If arbitrary faults are uncommon, we have a < f + 1 replica started reducing the overhead
+
+\subsection{Digest outputs} $f + 1$ matching outputs of a given task (maps or reduces) have to be received to be considered correct.
+However, tasks output can have considerable size be large therefore to move data from workers to leader is useless.
+can increse uselessly network traffic, worsening performance.
+
+Digest outputs. f + 1 matching outputs of maps or reduces
+have to be received to be considered correct. These outputs
+tend to be large, so it is useful to fetch one output from some
+task replica and compare just digests (hashes). This way, it is
+still possible to validate the output without generating much
+additional network traffic.
 

### 2019-08-30 sample-sigchi.tex
update

@@
-%%
-%% This is file `sample-sigchi.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigchi')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-sigchi.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
 \documentclass[sigchi]{acmart}
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
 \AtBeginDocument{%
@@
 
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
+\acmConference[]{}{}{}
+\acmBooktitle{}
 \acmPrice{15.00}
@@
 
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
 \begin{document}
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
 \title{Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce}
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
 \author{Andrea Graziani}
@@
 
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+\renewcommand{\shortauthors}{Andrea Graziani (0273395)}
 
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
 \begin{abstract}
@@
 Although the execution of a job with our algorithms uses more resources respect to other implementations, like Hadoop, we believe that this cost is acceptable for critical applications that require that level of fault tolerance.
-
 \end{abstract}
-
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{MapReduce, Fault tolerance, Arbitrary failure, Data locality}
 
@@
 
-An important goal in distributed-systems design is to construct a system in such a way it can provide its services even in the presence of faults. In other words, whenever a failure
-occurs, the system should continue to operate in an acceptable way; that is a distributed system is expected to be \textit{fault tolerant}.
-As known, many fault types exists in literature, the most serious of which are \textit{arbitrary failures}, also known as \textit{Byzantine failures}; whenever a that type of fault occurs, a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
+Nowadays many famous distributed applications use thousands of computers and hundreds of other devices like network switches, routers and power units in order to provide their services to an increasing number of users in every part of the world.
+
+Moreover there are various data-intensive task, like seismic simulation, natural language processing, machine learning, astronomical data parsing and web data mining, which require a processing power exceeds the capabilities of individual computers imposing the use of distributed computing.
+MapReduce, a framework developed by Google, represents a solution for processing large data sets.
+
+As many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future owing to the increasing number of computer and server connected to internet.
+Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures.
+A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{Abril07}.
+A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent \cite{Abril07}
+
+This is the reason why to construct a distributed system in such a way it can provide its services even in the presence of failures is become so critical for economic reasons; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.
+
+As known academic literature describes many type of failure, like \textit{crash failures}; however the most serious are known as \textit{arbitrary failures} or \textit{Byzantine failures}, according to which a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
+
+Often mostly all data-intensive tasks require large data sets moving between computers in order to operate correctly. Moving data repeatedly to distant nodes is becoming the bottleneck [23].
+
+Then the goal of this paper is to describe an Arbitrary Fault-Tolerant (AFT) MapReduce runtime system.
 
@@
 \endinput
-%%
-%% End of file `sample-sigchi.tex'.

### 2019-08-30 sample-sigchi.tex
update

@@
 
-Nowadays many famous distributed applications use thousands of computers and hundreds of other devices like network switches, routers and power units in order to provide their services to an increasing number of users in every part of the world.
+Various data-intensive tasks, like seismic simulation, natural language processing, machine learning, astronomical data parsing, web data mining and many other, require a processing power that exceeds the capabilities of individual computers; this fact imposes the use of \textit{distributed computing}.
+Nowadays many famous distributed applications use thousands of computers and hundreds of other devices like network switches, routers and power units in order to provide their services to an increasing number of users in every part of the world, moving consequently an huge amount of data between computers and server.
+\textit{MapReduce}, a framework developed by Google, represents a solution for processing large data sets in a distributed environment.
 
-Moreover there are various data-intensive task, like seismic simulation, natural language processing, machine learning, astronomical data parsing and web data mining, which require a processing power exceeds the capabilities of individual computers imposing the use of distributed computing.
-MapReduce, a framework developed by Google, represents a solution for processing large data sets.
-
-As many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future owing to the increasing number of computer and server connected to internet.
+However, as many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future owing to the increasing number of computer and server connected to internet.
 Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures.
 A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{Abril07}.
-A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent \cite{Abril07}
+A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent.
+\cite{Abril07} Moreover moving large amount of data repeatedly to distant nodes is becoming the bottleneck owing to an increased network traffic causing performance degradation.
 
-This is the reason why to construct a distributed system in such a way it can provide its services even in the presence of failures is become so critical for economic reasons; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.
+These are the reasons why to construct a distributed system in such a way it can provide its services even in the presence of failures is become so critical; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.
+Moreover exploiting data locality, in order to mitigate network traffic and delay, becomes very important to improve performance.
+
+Then the goal of this paper is to describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) \textit{MapReduce runtime system} capable to mitigate problems described above.
+
+\section{Arbitrary Fault-Tolerant Locality-Aware MapReduce}
 
 As known academic literature describes many type of failure, like \textit{crash failures}; however the most serious are known as \textit{arbitrary failures} or \textit{Byzantine failures}, according to which a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
-
-Often mostly all data-intensive tasks require large data sets moving between computers in order to operate correctly. Moving data repeatedly to distant nodes is becoming the bottleneck [23].
 

### 2019-08-30 sample-sigchi.tex
update

@@
 
+\subsection{Arbitrary fault tolerance}
+
 As known academic literature describes many type of failure, like \textit{crash failures}; however the most serious are known as \textit{arbitrary failures} or \textit{Byzantine failures}, according to which a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
 
-Then the goal of this paper is to describe an Arbitrary Fault-Tolerant (AFT) MapReduce runtime system.
+Redundancy represents the key technique used to manage these kind of failure, according to which,
 
-In this paper we present an Arbitrary Fault-Tolerant (AFT) MapReduce runtime system.
-
-The key technique used to manage faults is, as , to use redundancy.The key approach to tolerating a faulty process is to organize several identical processes into a group.
+The key approach to tolerating a faulty process is to organize several identical processes into a group.
 
@@
 
-\section{Template Overview}
+\section{System Architecture}
 
-\subsection{System Architecture}
+In order to properly describe our MapReduce algorithm, including our arbitrary failures management system and how we exploit data locality in order to improve performance, it is necessary to describe our system architecture.
 
-Our system is composed by a set of distributed processes:
+\subsection{Assumptions}
+
+Our system is composed by a set of distributed processes, every of which run on different hosts in a same data-center; from implementation point of view, every process run on his own Amazon EC2 server hosted in a same region.
+
+We assume that our system runs \textit{asynchronously}, that is no assumptions about process execution speeds or message delivery times are made; therefore we can normally use timeouts to conclude that a process has crashed but, occasionally, such conclusion is false.
+However, all processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by the use of TCP connections.
+
+Clients are always correct, because if they are not there is no point in worrying about the correctness of our system's output.
+
+Finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
+
+\subsection{System's processes}
+
+Our system is made up of three type of process:
+
+\begin{description}
+\item[Client Process] Which requests the execution of jobs composed by map and reduce tasks among
+
+\item[Primary Process] Its duty it to satisfy clients requests coordinating worker processes activities.
+
+\item[Worker Process] A Worker Process executes map and reduce task scheduleted by current Leader Primary Process.
+\end{description}
+
+ by a set of distributed processes:
 

### 2019-08-30 sample-sigchi.tex
update

@@
 
-\item[Primary Process] Its duty it to satisfy clients requests coordinating worker processes activities.
+\item[Primary Process] Similarly to \textit{JobTracker} process used in Apache Hadoop, its duty is to satisfy clients requests, scheduling \textit{map} and \textit{reduce} tasks, coordinating at the same time \textit{worker processes} activities.
 
-\item[Worker Process] A Worker Process executes map and reduce task scheduleted by current Leader Primary Process.
+\item[Worker Process] It executes map or reduce task scheduled by current primary process.
 \end{description}
+
+Unlike Hadoop, according to which the \textit{JobTracker} process is assumed always correct, the host where primary process is running may fail, for example by crashing or by losing network connectivity; in other words, primary process's host represents a \textit{single point of failure}.
+Therefore, to ensure an high system availability, we have adopted an architecture based on multiple primary process copies run on different host, one of which, using a leader election algorithm, is elected as system coordinator.
+When current leader fails, a backup copy is promoted to become the new coordinator.
+From an implementation point of view, we used services offered by Apache ZooKeeper to implement our leader election mechanism.
+
+In order to achieve its duty, current primary process leader stores various information about requests received by clients, like their status and other informations about worker processes activities.
+Is very important to specify that such data are stored in memory, therefore they are permanently lost after a crash; this design makes our system  easier to implement and helps to reducing overhead due to the disk I/O activities.
+However recover lost in-memory leader state after a failure is required in order to satisfy clients requests.
+During each step of MapReduce framework, current primary leader process save current client requests status using an external fault tolerant services, in our case Apache zookeeper.
+When a primary process backup becomes leader, it retrieves all data from Apache ZooKeeper, restarting all pending client request from last saved state.
+
+Current leader primary process can interact with worker processes using a push-based approach in order to schedule map or reduce tasks.
+
+\subsection{The algorithm}
+
+To make our system arbitrary fault-tolerant we have followed the approach according to which each task is executed more than once by different processes running on different host.
+This design requires to organize several identical processes into a group through which became possible to mask one or more faulty processes.
+
+As known, MapReduce framework splits input file in several splits to each of which a map task is associated; in other words, if an input file is split, for instance, into $n$ elements, primary process has to schedule $n$ map tasks.
+In order to achieve arbitrary fault-tolerance, each map task has to be executed by a groups of identical process performing given task.
+According to this design, in order to manage $n$ map tasks, $n$ different groups of processes are needed; these group are called Worker Groups.
+A worker group is a set of equal worker processes, each of which execute the same commands using same input data in the same order.
+In a group all worker processes run independently on different host and they do not interact with each other in any way.
+Current Leader Primary Process can interact with groups members using a push-based approach in order to schedule map or reduce tasks.
+This is the reason according to which this design is more expensive than using the original MapReduce runtime or Hadoop.
+
+To be more precise, suppose to have $n$ worker groups and to want tolerate at most $k$ faulty processes for each group.
+To achieve arbitrary fault-tolerance, we can apply, for instance, a consensus algorithm like Paxos or Raft in order to reach consensus among all processes belonging to a given worker group.
+However that solution is too expensive because it requires $3f + 1$ replicas; moreover if we have, for instance, $n$ worker groups, we need at least $n(3k + 1)$ processes.
+
+This is the reason accoridng to which we have adopt an 
+An important issue with this design is how much replication is needed.
+As known, if processes exhibit arbitrary failures, continuing to run when faulty and sending out erroneous or random replies, a minimum of $2k+1$ processes are needed to achieve $k$-fault tolerance.
+In the worst case, the $k$ failing processes could accidentally generate the same reply.
+However, the remaining $k+1$ will also produce the same answer, so the primary process just believe the majority.
+Notice that, for instance, applying consensus algorithm to reach consensus among k group members may suffer from fail-arbitrary failures requires 3f + 1 replicas to tolerate at most f faulty replicas.
+
+ we have discarded this option considering it too expensive through which
+
+,
+
+In replicated-write protocols, an update is forwarded to several replicas at the same time.
+
+  we have a group of 3k+1 processes.
+Our goal is to show that we can establish a solution in which k group members may suffer from fail-arbitrary failures, yet the remaining nonfaulty processes will still reach consensus
+
+All worker processes are running are logically split into several \textit{Groups}, that is sets of equal worker processes, each of which execute the same commands using same input data in the same order.
+In a group all worker processes run independently on different host and they do not interact with each other in any way.
+Current Leader Primary Process can interact with groups members using a push-based approach in order to schedule map or reduce tasks.
+Although, for performance reasons, not always happen, when a task is sent to the group itself, all members of the group receive it.
+
+ Notice that, for instance, the state machine approach requires 3f + 1 replicas to tolerate at most f faulty replicas,
+
+. First,theJobTrackerstarts 2f +1
 
@@
 In our implementation, each process run on independent Amazon EC2 server
+
+The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover.
+This helps the Mesos master scale to large clusters with many tasks and frameworks.
+A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.
 
@@
 \end{description}
-
-We assume that clients are always correct, because if they are not there is no point in worrying about the correctness of the job’s output.
-
-The host where current master process is running may fail, for example by crashing or by losing network connectivity.
-Therefore, to ensure system availability in such a way that it can keep on providing its services, multiple master process copies of run on different host, and that a backup copy is promoted to become the new leader when the previous leader fails.
-
-In order to decide when the current leader master process has failed and to elect a new leader, we have used a coordination service like Apache ZooKeeper.
-
-The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover.
-This helps the Mesos master scale to large clusters with many tasks and frameworks.
-A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.
-
- Mesos consists of a master daemon that manages agent daemons running on each cluster node, and Mesos frameworks that run tasks on these agents.
-
-The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover.
-This helps the Mesos master scale to large clusters with many tasks and frameworks.
-A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.
-
-System model. The system is composed by a set of dis-
-tributed processes: the clients that request the execution of
-jobs composed by map and reduce tasks, the JobTracker that
-manages the execution of a job as explained, a set of Task-
-Trackers that execute tasks, the NameNode that manages ac-
-cess to data stored in HDFS, and a set of DataNodes where
-HDFS stores file blocks. We say that a process is correct if
-it follows the algorithm, otherwise we say it is faulty. We
-also use these two words to denominate a task (map or re-
-duce) that, respectively, returns the result that corresponds to
-an execution in a correct TaskTracker (correct) or not (faulty).
-Processes run in servers in a datacenter.
 

### 2019-08-31 sample-sigchi.tex
update

@@
 
-This is the reason accoridng to which we have adopt an 
+This is the reason according to which we have adopt an 
 An important issue with this design is how much replication is needed.
@@
 
- Notice that, for instance, the state machine approach requires 3f + 1 replicas to tolerate at most f faulty replicas,
+\subsection{Digest outputs} As explained above, in order to consider a task correct, tolerating at most $f$ faulty processes, we need $f + 1$ matching outputs have to be received.
 
-. First,theJobTrackerstarts 2f +1
+To validate task's output, since outputs computed by worker processes can be very large, in order to avoid pointless additional network traffic, we have adopted an approach according to which primary process fetches and compares outputs \textit{digests} from all workers within a group; this design allows us to increase system's performance.
+
+\subsection{Crash failure detection} To manage and detect workers processes crash faults we have use some features of Apache Zookeeper.
+
+As known, Apache ZooKeeper has the notion of \textit{ephemeral nodes}, that is special znodes which exists as long as the \textit{session} that created the znode is active.
+When session expiration occurs, Zookeeper cluster will delete all ephemeral nodes owned by that session and immediately notify all connected clients of the change.
+
+When any client establishes a session with a Zookeeper cluster, a time-out value is used by the cluster to determine when the client's session expires.
+Expirations usually happens when the cluster does not hear from the client within the specified session time-out period (i.e.
+no heartbeat).
+
+Notice that session is kept alive by requests sent by client, therefore is critical that client will send PING request to keep the session alive.
+This PING request not only allows the ZooKeeper server to know that the client is still active, but it also allows the client to verify that its connection to the ZooKeeper server is still active.
+
+Using this design, is very easy to keep check the status of worker processes.
+
+\subsection{Deferred execution} We believe that there is no point in always executing $2f + 1$ replicas for each task to usually obtain the same result.
+
+To minimize both the number of copies of tasks executed and the overhead due to network traffic, saving also some energy, we have adopted a design called \textit{Deferred Execution}: according to that solution current primary starts only $f + 1$ replicas of the same task, checking if they all return the same result.
+If a time-out elapses, or some returned results do not match, more replicas (up to $f$) are started, until there are $f + 1$ matching replies.
+
+Supposing that Byzantine faults are uncommon, this design reduce the overhead introduced by the basic scheme.
+
+\subsection{Data locality awareness}
+
+Since moving data repeatedly among nodes is bottleneck, to improve MapReduce performance, we have adopt a design aware of data locations and sizes in order to mitigate network traffic.
+
+Our solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}".
+When the map phase is fully done, all the network locations of the feeding nodes of every reducer will be known
+
+Moving data repeatedly to distant nodes is becoming the bottleneck [23].
+In this paper we rethink reduce task scheduling in Hadoop and suggest making Hadoop’s reduce task scheduler aware of partitions’ network locations and sizes in order to mitigate network trafﬁc.
+
+A key question is how to schedule reduce tasks at Task Trackers so as to diminish shufﬂed data and improve MapReduce performance.
+One of Hadoop’s basic principles is: ”moving computation towards data is cheaper than moving data towards computation”.
+Such a principle is employed by Hadoop when scheduling map tasks but bypassed when scheduling reduce tasks.
+MapReduce is aware of the network locations of splits (inputstomappers)andleveragessuchinformationtoschedule mappers nearby splits.
+In contrast, MapReduce is oblivious to the network locations of partitions (inputs to reducers) and does not schedule reducers nearby partitions.
+Thus, similar to map task scheduling, we suggest making MapReduce aware of partitions’ network locations in order to apply locality to reduce task scheduling
+
+As we will be able to explain later, this design allows us to exploit data locality to increase system performance; in fact, when
 
@@
 
-\subsection{Crash failure detection} Workers nodes crash faults are detected using ZooKeeper's coordination service.
-As known, ZooKeeper allows users to store persistently coordination data into several hierarchically grouped nodes, called \textit{znode}.
-However, ZooKeeper has the notion of \textit{ephemeral nodes} too; these special znodes exists as long as the session that created the znode is active, that is when the session ends the znode is deleted.
-A ZooKeeper client establishes a session with the ZooKeeper service
-
-At session expiration the cluster will delete any/all ephemeral nodes owned by that session and immediately notify any/all connected clients of the change
-
-In this way, is very easy to keep check the status of worker nodes by current primary process.
-If any of worker node crash, ZooKeeper automatically delete znode associated to crashed server and notifies current leader.
+\subsection{Crash failure detection}
 
@@
 In the best case, without Byzantine faults, only f + 1 replicas are started. If arbitrary faults are uncommon, we have a < f + 1 replica started reducing the overhead
-
-\subsection{Digest outputs} $f + 1$ matching outputs of a given task (maps or reduces) have to be received to be considered correct.
-However, tasks output can have considerable size be large therefore to move data from workers to leader is useless.
-can increse uselessly network traffic, worsening performance.
-
-Digest outputs. f + 1 matching outputs of maps or reduces
-have to be received to be considered correct. These outputs
-tend to be large, so it is useful to fetch one output from some
-task replica and compare just digests (hashes). This way, it is
-still possible to validate the output without generating much
-additional network traffic.
 

### 2019-09-02 sample-sigchi.tex
update

@@
 
-\acmConference[]{}{}{}
-\acmBooktitle{}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-9999-9/18/06}
+\settopmatter{printacmref=false, printccs=false, printfolios =false}
+\setcopyright{none} 
+\renewcommand\footnotetextcopyrightpermission[1]{}
+
+\acmConference[SDCC Project A.A. 2018-2019]{ }{September 18, 2019}{ }
 
@@
 \begin{abstract}
-MapReduce is often used to run critical jobs such as scientific data analysis.
-However, evidence in the literature shows that arbitrary faults do occur and can probably corrupt the results of MapReduce jobs; Moreover, ignoring data locality during task scheduling can lead to performance degradation and a pointless bigger network traffic.
+\textit{MapReduce} is a programming paradigm that enables massive scalability across hundreds or thousands of servers allowing to process very large data set \cite{IBMWhatIsMapReduce}
+
+However, evidence in the literature shows that arbitrary faults do occur and can probably corrupt the results of MapReduce jobs\cite{MicrosoftStudyFailure}; Moreover, ignoring data locality during task scheduling can lead to performance degradation and a pointless bigger network traffic.
 
@@
 
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
 \keywords{MapReduce, Fault tolerance, Arbitrary failure, Data locality}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
 \maketitle
@@
 Moving data repeatedly to distant nodes is becoming the bottleneck [23].
-In this paper we rethink reduce task scheduling in Hadoop and suggest making Hadoop’s reduce task scheduler aware of partitions’ network locations and sizes in order to mitigate network trafﬁc.
+In this paper we rethink reduce task scheduling in Hadoop and suggest making Hadoop’s reduce task scheduler aware of partitions’ network locations and sizes in order to mitigate network traffic.
 
-A key question is how to schedule reduce tasks at Task Trackers so as to diminish shufﬂed data and improve MapReduce performance.
-One of Hadoop’s basic principles is: ”moving computation towards data is cheaper than moving data towards computation”.
+A key question is how to schedule reduce tasks at Task Trackers so as to diminish shuffled data and improve MapReduce performance.
+One of Hadoop’s basic principles is: moving computation towards data is cheaper than moving data towards computation.
 Such a principle is employed by Hadoop when scheduling map tasks but bypassed when scheduling reduce tasks.
@@
 In contrast, MapReduce is oblivious to the network locations of partitions (inputs to reducers) and does not schedule reducers nearby partitions.
-Thus, similar to map task scheduling, we suggest making MapReduce aware of partitions’ network locations in order to apply locality to reduce task scheduling
+Thus, similar to map task scheduling, we suggest making MapReduce aware of partitions network locations in order to apply locality to reduce task scheduling
 
@@
 
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigchi]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for all short- and
-full-length articles, and optional for two-page abstracts.
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
-  doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
 \bibliographystyle{ACM-Reference-Format}
@@
 
-%%
-%% If your work has an appendix, this is the place to put it.
 \appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
 

### 2019-09-02 sample-sigchi.tex
update

@@
 \begin{abstract}
-\textit{MapReduce} is a programming paradigm that enables massive scalability across hundreds or thousands of servers allowing to process very large data set \cite{IBMWhatIsMapReduce}
+\textit{MapReduce} is a programming paradigm that enables massive scalability across hundreds or thousands of servers allowing to process very large data-set \cite{IBMWhatIsMapReduce}.
 
-However, evidence in the literature shows that arbitrary faults do occur and can probably corrupt the results of MapReduce jobs\cite{MicrosoftStudyFailure}; Moreover, ignoring data locality during task scheduling can lead to performance degradation and a pointless bigger network traffic.
+Both academic literature and daily experience shows that \textit{arbitrary faults} frequently occur corrupting our results \cite{BFLMapReduce}.
+Moreover, ignore data-set locality can lead to performance degradation and a pointless bigger network traffic \cite{LARTS}.
 
-We present an original MapReduce algorithm capable to tolerate arbitrary or Byzantine faults experienced by worker nodes and to resolve master node single point of failure problem; moreover, recognizing input data network locations and sizes, our algorithm performs a locality aware task scheduling, improving performance and diminishing network traffic.
+In this paper we present an original MapReduce runtime system capable both to tolerate arbitrary faults and to recognize input data network locations and sizes in order to perform a \textit{locality-aware task scheduling}, improving performance and diminishing network traffic.
 
-Although the execution of a job with our algorithms uses more resources respect to other implementations, like Hadoop, we believe that this cost is acceptable for critical applications that require that level of fault tolerance.
+Although job's execution using our system requires more resources respect to other implementations, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
 \end{abstract}
@@
 However, as many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future owing to the increasing number of computer and server connected to internet.
-Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures.
-A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{Abril07}.
+Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures \cite{PetaScaleFailure}.
+A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{DRAMError}.
 A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent.
-\cite{Abril07} Moreover moving large amount of data repeatedly to distant nodes is becoming the bottleneck owing to an increased network traffic causing performance degradation.
+\cite{MicrosoftStudyFailure} Moreover moving large amount of data repeatedly to distant nodes is becoming the bottleneck owing to an increased network traffic causing performance degradation.
 
@@
 
-Finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
+finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
 

### 2019-09-02 sample-sigchi.tex
update

@@
 \begin{abstract}
-\textit{MapReduce} is a programming paradigm that enables massive scalability across hundreds or thousands of servers allowing to process very large data-set \cite{IBMWhatIsMapReduce}.
+\textit{MapReduce} is a programming paradigm developed by Google that enables massive scalability across hundreds or thousands of servers allowing to process very large data-set \cite{IBMWhatIsMapReduce}.
 
@@
 
-Various data-intensive tasks, like seismic simulation, natural language processing, machine learning, astronomical data parsing, web data mining and many other, require a processing power that exceeds the capabilities of individual computers; this fact imposes the use of \textit{distributed computing}.
-Nowadays many famous distributed applications use thousands of computers and hundreds of other devices like network switches, routers and power units in order to provide their services to an increasing number of users in every part of the world, moving consequently an huge amount of data between computers and server.
-\textit{MapReduce}, a framework developed by Google, represents a solution for processing large data sets in a distributed environment.
+Various data-intensive tasks, like seismic simulation, natural language processing, machine learning, astronomical data parsing, web data mining and many other, require a processing power that exceeds the capabilities of individual computers imposing the use of a \textit{distributed computing} \cite{LARTS}.
 
-However, as many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future owing to the increasing number of computer and server connected to internet.
+Nowadays many famous distributed applications use MapReduce framework as solution for processing large data sets in a distributed environment.
+In order to properly provide services to an increasing number of users worldwide, is necessary to connect together thousands of computers and hundreds of other devices like network switches, routers and power units, moving consequently an huge amount of data between computers.
+
+However, as many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future due to increasing number of computers connected to internet \citep{BFLMapReduce}.
 Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures \cite{PetaScaleFailure}.
@@
 
-These are the reasons why to construct a distributed system in such a way it can provide its services even in the presence of failures is become so critical; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.
-Moreover exploiting data locality, in order to mitigate network traffic and delay, becomes very important to improve performance.
+Therefore to construct a distributed system capable to provide its services even in the presence of failures is become so critical; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.
 
-Then the goal of this paper is to describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) \textit{MapReduce runtime system} capable to mitigate problems described above.
+Moreover, due to very large data-set involved during data-intensive tasks, exploiting data locality, in order to mitigate network traffic and delay, becomes very important to improve performance.
 
-\section{Arbitrary Fault-Tolerant Locality-Aware MapReduce}
+In these paper we will describe our \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system capable to resolve all issues described above.
+We implemented our AFTLA MapReduce system from scratch using Go programming language, adopting Apache ZooKeeper\textsuperscript{TM} to provide service for maintaining configuration information and system coordination \footnote{See \url{https://zookeeper.apache.org}}.
+All libraries used in our implementation are fully described in table \ref{tab:libraries}.
 
-\subsection{Arbitrary fault tolerance}
-
-As known academic literature describes many type of failure, like \textit{crash failures}; however the most serious are known as \textit{arbitrary failures} or \textit{Byzantine failures}, according to which a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
-
-Redundancy represents the key technique used to manage these kind of failure, according to which,
-
-The key approach to tolerating a faulty process is to organize several identical processes into a group.
-
- Our BFT
-MapReduce follows the approach of executing each task more
-than once, similarly to the works mentioned above. The chal-
-
-Process groups are part of the solution for building fault-tolerant systems.
-In particular, having a group of identical processes allows us to mask one
-or more faulty processes in that group. In other words, we can replicate
-processes and organize them into a group to replace a single (vulnerable)
-process with a (fault tolerant) group.
-
-An important issue with using process groups to tolerate faults is how
-much replication is needed. To simplify our discussion, let us consider
-only replicated-write systems. A system is said to be k-fault tolerant if it
-can survive faults in k components and still meet its specifications. If the
-components, say processes, fail silently, then having k + 1 of them is enough
-to provide k-fault tolerance. If k of them simply stop, then the answer from
-the other one can be used.
-
-On the other hand, if processes exhibit arbitrary failures, continuing to
-run when faulty and sending out erroneous or random replies, a minimum
-of 2k + 1 processes are needed to achieve k-fault tolerance. In the worst case,
-the k failing processes could accidentally (or even intentionally) generate the
-same reply. However, the remaining k + 1 will also produce the same answer,
-so the client or voter can just believe the majority.
+\begin{table*}
+  \caption{Libraries used in our implementation}
+  \label{tab:libraries}
+  \begin{tabular}{l|l|l}
+    \toprule
+    Name & Description & Link \\
+    \midrule
+    \texttt{go-zookeeper/go} & Native Go Zookeeper Client Library & \url{https://github.com/samuel/go-zookeeper} \\
+    \texttt{logrus} & A structured logger for Go & \url{https://github.com/Sirupsen/logrus} \\
+    \texttt{aws-sdk-go} & AWS SDK for the Go programming language. & \url{https://github.com/aws/aws-sdk-go} \\
+    \bottomrule
+  \end{tabular}
+\end{table*}
 
@@
 
-In order to properly describe our MapReduce algorithm, including our arbitrary failures management system and how we exploit data locality in order to improve performance, it is necessary to describe our system architecture.
+In order to properly describe how our algorithm can tolerate arbitrary faults and to exploit data locality, it is necessary to describe its architecture.
 
@@
 
-Our system is composed by a set of distributed processes, every of which run on different hosts in a same data-center; from implementation point of view, every process run on his own Amazon EC2 server hosted in a same region.
+Let's start our description making some very important assumptions.
 
-We assume that our system runs \textit{asynchronously}, that is no assumptions about process execution speeds or message delivery times are made; therefore we can normally use timeouts to conclude that a process has crashed but, occasionally, such conclusion is false.
-However, all processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by the use of TCP connections.
+Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center; from an implementation point of view, every process run on his own Amazon EC2 server hosted in a same region (\texttt{us-east-1}).
+All processes interact with each other using RPC
 
-Clients are always correct, because if they are not there is no point in worrying about the correctness of our system's output.
+We assume that our system runs \textit{asynchronously}, that is no assumptions about process execution speeds or message delivery times are made; therefore we can normally use timeouts to state that a process has crashed although, occasionally, such conclusion is false \cite{SDCC}.
 
-finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
+All processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by TCP connections.
+
+Clients are \textit{always correct}, because if they are not there is no point in worrying about the correctness of our system's output.
+
+Finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
 
@@
 
+\section{Arbitrary Fault-Tolerant Locality-Aware MapReduce}
+
+\subsection{Arbitrary fault tolerance}
+
+As known academic literature describes many type of failure, like \textit{crash failures}; however the most serious are known as \textit{arbitrary failures} or \textit{Byzantine failures}, according to which a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
+
+Redundancy represents the key technique used to manage these kind of failure, according to which,
+
+The key approach to tolerating a faulty process is to organize several identical processes into a group.
+
+ Our BFT
+MapReduce follows the approach of executing each task more
+than once, similarly to the works mentioned above. The chal-
+
+Process groups are part of the solution for building fault-tolerant systems.
+In particular, having a group of identical processes allows us to mask one
+or more faulty processes in that group. In other words, we can replicate
+processes and organize them into a group to replace a single (vulnerable)
+process with a (fault tolerant) group.
+
+An important issue with using process groups to tolerate faults is how
+much replication is needed. To simplify our discussion, let us consider
+only replicated-write systems. A system is said to be k-fault tolerant if it
+can survive faults in k components and still meet its specifications. If the
+components, say processes, fail silently, then having k + 1 of them is enough
+to provide k-fault tolerance. If k of them simply stop, then the answer from
+the other one can be used.
+
+On the other hand, if processes exhibit arbitrary failures, continuing to
+run when faulty and sending out erroneous or random replies, a minimum
+of 2k + 1 processes are needed to achieve k-fault tolerance. In the worst case,
+the k failing processes could accidentally (or even intentionally) generate the
+same reply. However, the remaining k + 1 will also produce the same answer,
+so the client or voter can just believe the majority.
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-09-03 sample-sigchi.tex
update

@@
 In these paper we will describe our \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system capable to resolve all issues described above.
-We implemented our AFTLA MapReduce system from scratch using Go programming language, adopting Apache ZooKeeper\textsuperscript{TM} to provide service for maintaining configuration information and system coordination \footnote{See \url{https://zookeeper.apache.org}}.
-All libraries used in our implementation are fully described in table \ref{tab:libraries}.
+We have implemented an AFTLA MapReduce system, capable to perform a word-count of a given text input, from scratch using Go programming language, adopting Apache ZooKeeper\textsuperscript{TM} for maintaining configuration information and system coordination \footnote{See \url{https://zookeeper.apache.org}}; all libraries used in our implementation are fully described in table \ref{tab:libraries}.
+Our prototype    's source code is fully available on GitHub\footnote{See \url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.
 
@@
 
-\section{System Architecture}
+\section{Assumptions}
 
 In order to properly describe how our algorithm can tolerate arbitrary faults and to exploit data locality, it is necessary to describe its architecture.
+To do that, in this section we start making some very important assumptions.
 
-\subsection{Assumptions}
-
-Let's start our description making some very important assumptions.
-
-Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center; from an implementation point of view, every process run on his own Amazon EC2 server hosted in a same region (\texttt{us-east-1}).
+Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center; in our prototype, every process run on his own Amazon EC2 server hosted in a same region (\texttt{us-east-1}).
 All processes interact with each other using RPC
@@
 All processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by TCP connections.
+All system processes use RPC protocol in order to interact with each other.
 
 Clients are \textit{always correct}, because if they are not there is no point in worrying about the correctness of our system's output.
-
 Finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
 
-\subsection{System's processes}
+In this paper, we take for granted reader's knowledge of the MapReduce framework and Hadoop implementation. framework.
 
-Our system is made up of three type of process:
+\section{System's processes}
+
+Three kind of process are used in our system:
 
 \begin{description}
-\item[Client Process] Which requests the execution of jobs composed by map and reduce tasks among
+\item[Client Processes] Which send word-count requests to our system sending directly an input text file.
 
-\item[Primary Process] Similarly to \textit{JobTracker} process used in Apache Hadoop, its duty is to satisfy clients requests, scheduling \textit{map} and \textit{reduce} tasks, coordinating at the same time \textit{worker processes} activities.
+\item[Worker Process (WP)] They execute \textit{map} or \textit{reduce} scheduled by LPP.
 
-\item[Worker Process] It executes map or reduce task scheduled by current primary process.
+\item[Primary Process (PP)] It is similar to \textit{JobTracker} process used in Apache Hadoop which duty is to satisfy clients requests scheduling \textit{map} or \textit{reduce} tasks. 
 \end{description}
 
-Unlike Hadoop, according to which the \textit{JobTracker} process is assumed always correct, the host where primary process is running may fail, for example by crashing or by losing network connectivity; in other words, primary process's host represents a \textit{single point of failure}.
-Therefore, to ensure an high system availability, we have adopted an architecture based on multiple primary process copies run on different host, one of which, using a leader election algorithm, is elected as system coordinator.
-When current leader fails, a backup copy is promoted to become the new coordinator.
-From an implementation point of view, we used services offered by Apache ZooKeeper to implement our leader election mechanism.
+\subsection{Primary Process}
+At this point, is necessary to make some clarifications about PP's features.
 
-In order to achieve its duty, current primary process leader stores various information about requests received by clients, like their status and other informations about worker processes activities.
-Is very important to specify that such data are stored in memory, therefore they are permanently lost after a crash; this design makes our system  easier to implement and helps to reducing overhead due to the disk I/O activities.
+Unlike Hadoop, according to which \textit{JobTracker} process is assumed always correct, the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents a \textit{single point of failure}.
+
+Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on different machines; using any leader election algorithm, is possible to elect one of these copies as \textit{Leader Primary Process} (LPP) while all the others remain on stand-by.
+Using this approach, is possible to manage PP crash failure: when current leader fails, a backup copy is promoted to become the new .
+
+LPP represents our system coordinator since only it can can interact with WP scheduling task using a \textit{push-based} approach (unlike Hadoop according to which JobTracker schedules task using a \textit{pull-based} approach \cite{LARTS})
+
+However, to perform its task, LPP manages various information about clients requests, many of which, as we will see later, are sent by WP after a map or reduce task.
+In other word, LPP has got a status.
+
+Is very important to specify that LPP status is stored in memory, therefore they are permanently lost after a crash; this design makes our system easier to implement and helps to reducing overhead due to the disk I/O activities.
 However recover lost in-memory leader state after a failure is required in order to satisfy clients requests.
-During each step of MapReduce framework, current primary leader process save current client requests status using an external fault tolerant services, in our case Apache zookeeper.
-When a primary process backup becomes leader, it retrieves all data from Apache ZooKeeper, restarting all pending client request from last saved state.
 
-Current leader primary process can interact with worker processes using a push-based approach in order to schedule map or reduce tasks.
+Therefore we have adopt a design according to which LPP make a sort of backup, or snapshot, of its current state regularly.
+To make our implementation easier, in our prototype, considering that LPP state contains a very small amount of data, LPP stores its state in a Zookeeper cluster after some events, like a map task termination.
+In case of crash failure of current LPP, when a primary process backup becomes leader, it retrieves all data from Apache ZooKeeper cluster, recovering last saved state.
+
+\subsection{Worker Process}
 
@@
 As we will be able to explain later, this design allows us to exploit data locality to increase system performance; in fact, when
+
+From an implementation point of view, we used services offered by Apache ZooKeeper to implement our leader election mechanism.
 

### 2019-09-03 sample-sigchi.tex
update

@@
 
-\subsection{Worker Process}
+\subsection{Worker Process and Groups}
 
-\subsection{The algorithm}
+To make WP arbitrary fault-tolerant we have adopt a design according to which each task (map, reduce, etc.) is executed more than once by different processes running on different host.
+This approach requires to organize all our WPs into several \textit{groups} through which became possible to mask one or more faulty processes of a given group.
 
-To make our system arbitrary fault-tolerant we have followed the approach according to which each task is executed more than once by different processes running on different host.
-This design requires to organize several identical processes into a group through which became possible to mask one or more faulty processes.
+Before explaining how we manage WP faults, we must explain what is a Worker Processes Group (WPG).
+A WPG is a set of identical worker processes, each of which execute, relatively to a given job, \textit{the same commands using the same input data in the same order}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.
+All commands and data are sent by LPP.
 
-As known, MapReduce framework splits input file in several splits to each of which a map task is associated; in other words, if an input file is split, for instance, into $n$ elements, primary process has to schedule $n$ map tasks.
-In order to achieve arbitrary fault-tolerance, each map task has to be executed by a groups of identical process performing given task.
-According to this design, in order to manage $n$ map tasks, $n$ different groups of processes are needed; these group are called Worker Groups.
-A worker group is a set of equal worker processes, each of which execute the same commands using same input data in the same order.
-In a group all worker processes run independently on different host and they do not interact with each other in any way.
-Current Leader Primary Process can interact with groups members using a push-based approach in order to schedule map or reduce tasks.
-This is the reason according to which this design is more expensive than using the original MapReduce runtime or Hadoop.
+Suppose to want tolerate at most $f$ arbitrary failures of all WPs belonging to a given group.
 
-To be more precise, suppose to have $n$ worker groups and to want tolerate at most $k$ faulty processes for each group.
-To achieve arbitrary fault-tolerance, we can apply, for instance, a consensus algorithm like Paxos or Raft in order to reach consensus among all processes belonging to a given worker group.
-However that solution is too expensive because it requires $3f + 1$ replicas; moreover if we have, for instance, $n$ worker groups, we need at least $n(3k + 1)$ processes.
+To achieve that level of fault-tolerance, we can apply to reach, for instance, \textit{byzantine agreement} among all processes belonging to group.
+However we believe that solution is too expensive because it requires, as properly explain in literature\citep{SDCC}, $3f + 1$ replicas.
 
-This is the reason according to which we have adopt an 
-An important issue with this design is how much replication is needed.
-As known, if processes exhibit arbitrary failures, continuing to run when faulty and sending out erroneous or random replies, a minimum of $2k+1$ processes are needed to achieve $k$-fault tolerance.
-In the worst case, the $k$ failing processes could accidentally generate the same reply.
-However, the remaining $k+1$ will also produce the same answer, so the primary process just believe the majority.
-Notice that, for instance, applying consensus algorithm to reach consensus among k group members may suffer from fail-arbitrary failures requires 3f + 1 replicas to tolerate at most f faulty replicas.
+Therefore we have adopt a protocol based on \textit{majority voting} inspired to quorum-based protocols applied in replicated-write systems.
+As explained in literature\citep{SDCC}, in this kind of systems, if processes exhibit arbitrary failures, continuing to run when faulty and sending out erroneous or random replies, a minimum of $2f+1$ processes are needed to achieve $f$-fault tolerance.
+In the worst case, the $f$ failing processes could accidentally generate the same reply.
+However, the remaining $f+1$ will also produce the same answer, so the LPP just believes the majority.
 
- we have discarded this option considering it too expensive through which
+In our design each map or reduce task scheduled by current LPP are assigned to independent WPGs.
+Let's try to explain this statement formally using map task as example (but is the same of any task).
+Let $i = 1,2,3...n$, where $n \in \mathbb{Z}_+$.
+As MapReduce framework states, our system splits the input text file $S$ in $n$ parts $\lbrace s_1, s_2, ...
+s_n \rbrace$ called \textit{split}; each split $s_i$ is associated to a map task $m_i \in \lbrace m_1, m_2, ...
+m_n \rbrace$ every of which must be replicated on multiple WPs to make them arbitrary fault tolerant.
+Each map task $m_i$ is assigned to a different WPG $g_i \in \lbrace g_1, g_2, ...
+g_n \rbrace$.
+As we will explain later, LPP, checking received outputs from each group, we can achieve arbitrary fault tolerance for every scheduled task.
+Obliviously to tolerate at most $f$ arbitrary failures of each task, each WPG must contains at least $2f+1$ different processes.
+Then our design requires at least $n(2f+1)$ different WPs.
 
-,
+This design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs.
+If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG, increasing the number PP backups too.
 
-In replicated-write protocols, an update is forwarded to several replicas at the same time.
-
-  we have a group of 3k+1 processes.
-Our goal is to show that we can establish a solution in which k group members may suffer from fail-arbitrary failures, yet the remaining nonfaulty processes will still reach consensus
-
-All worker processes are running are logically split into several \textit{Groups}, that is sets of equal worker processes, each of which execute the same commands using same input data in the same order.
-In a group all worker processes run independently on different host and they do not interact with each other in any way.
-Current Leader Primary Process can interact with groups members using a push-based approach in order to schedule map or reduce tasks.
-Although, for performance reasons, not always happen, when a task is sent to the group itself, all members of the group receive it.
+\section{Architecture }
 

### 2019-09-03 Paper.tex
update

--- 2019-09-03 sample-sigchi.tex
@@
 
-\section{System's processes}
+\section{System's model}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{Architecture}
+  \caption{System Architecture}
+\end{figure}
 
@@
 
-\section{Architecture }
+\section{The algorithm}
 
-\subsection{Digest outputs} As explained above, in order to consider a task correct, tolerating at most $f$ faulty processes, we need $f + 1$ matching outputs have to be received.
+Given the system model described previously, a solution to tolerate at most $f$ arbitrary faults during each task would be the following: current LPP assigns a given map/reduce task to a WPG contacting its $2f + 1$ WPs; then, after retrieving the outputs from replicas, picks the most voted results which is expected correct if no more than $f$ arbitrary faults occur.
 
-To validate task's output, since outputs computed by worker processes can be very large, in order to avoid pointless additional network traffic, we have adopted an approach according to which primary process fetches and compares outputs \textit{digests} from all workers within a group; this design allows us to increase system's performance.
+This simplistic solution is very expensive because it replicates everything $2f + 1$ times: task execution, communication of map task outputs and so on.
+We use a set of techniques to avoid these costs and do things efficiently:
+
+\subsection{Digest outputs} As explained above, in order to consider a map/reduce task correct, tolerating at most $f$ faulty processes, $f + 1$ matching outputs, coming from at least $2f + 1$ WPs belonging to a given WPG,  have to be received.
+
+To validate task's output, since outputs computed by worker processes can be very large, in order to avoid pointless additional network traffic, we have adopted an approach according to which LPP fetches and compares \textit{digests}, a bit string of a fixed size obtained using a hash function.
+The main advantage of this technique is that, digest size are many times smaller than task's data output, allowing us to reduce network traffic among servers, increasing system's performance.
+
+\subsection{Deferred execution} We believe that there is no point in always executing $2f + 1$ replicas for each task to usually obtain the same result.
+
+To minimize both the number of copies of tasks executed and the overhead due to network traffic we have adopted a design called \textit{deferred execution}: according to that solution current LPP starts only $f + 1$ replicas of the same task, checking if they all return the same result.
+If a time-out elapses, or some returned results do not match, more replicas (up to $f$) are started, until there are $f + 1$ matching replies.
+
+We believe that this this design is also energy-saver and cost-effective since, supposing that arbitrary faults are uncommon, fewer WP are involved into computations respect to basic scheme and, in principle, is possible to start and use a fewer number of servers using auto-scaling techniques (at cost of some latency).
+
+\subsection{Data locality awareness}
+
+Since in order to achieve fault tolerance we have replicate all task $2f + 1$ times, data transfers among servers are replicated too, generating an huge amount of network traffic.
+Evidently, when large data set are involved, move data repeatedly among server became a bottleneck.
+
+Therefore we have adopted a design capable to reduce
+
+Since moving data repeatedly among server is bottleneck, especially when large data set are involved, in order to improve system performance, we have adopt a design aware of data locations and sizes in order to mitigate network traffic avoiding pointless data moving.
+
+Our solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}".
+When the map phase is fully done, all the network locations of the feeding nodes of every reducer will be known
+
+Moving data repeatedly to distant nodes is becoming the bottleneck [23].
+In this paper we rethink reduce task scheduling in Hadoop and suggest making Hadoop’s reduce task scheduler aware of partitions’ network locations and sizes in order to mitigate network traffic.
+
+A key question is how to schedule reduce tasks at Task Trackers so as to diminish shuffled data and improve MapReduce performance.
+One of Hadoop’s basic principles is: moving computation towards data is cheaper than moving data towards computation.
+Such a principle is employed by Hadoop when scheduling map tasks but bypassed when scheduling reduce tasks.
+MapReduce is aware of the network locations of splits (inputstomappers)andleveragessuchinformationtoschedule mappers nearby splits.
+In contrast, MapReduce is oblivious to the network locations of partitions (inputs to reducers) and does not schedule reducers nearby partitions.
+Thus, similar to map task scheduling, we suggest making MapReduce aware of partitions network locations in order to apply locality to reduce task scheduling
 
@@
 
-\subsection{Deferred execution} We believe that there is no point in always executing $2f + 1$ replicas for each task to usually obtain the same result.
-
-To minimize both the number of copies of tasks executed and the overhead due to network traffic, saving also some energy, we have adopted a design called \textit{Deferred Execution}: according to that solution current primary starts only $f + 1$ replicas of the same task, checking if they all return the same result.
-If a time-out elapses, or some returned results do not match, more replicas (up to $f$) are started, until there are $f + 1$ matching replies.
-
-Supposing that Byzantine faults are uncommon, this design reduce the overhead introduced by the basic scheme.
-
-\subsection{Data locality awareness}
-
-Since moving data repeatedly among nodes is bottleneck, to improve MapReduce performance, we have adopt a design aware of data locations and sizes in order to mitigate network traffic.
-
-Our solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}".
-When the map phase is fully done, all the network locations of the feeding nodes of every reducer will be known
-
-Moving data repeatedly to distant nodes is becoming the bottleneck [23].
-In this paper we rethink reduce task scheduling in Hadoop and suggest making Hadoop’s reduce task scheduler aware of partitions’ network locations and sizes in order to mitigate network traffic.
-
-A key question is how to schedule reduce tasks at Task Trackers so as to diminish shuffled data and improve MapReduce performance.
-One of Hadoop’s basic principles is: moving computation towards data is cheaper than moving data towards computation.
-Such a principle is employed by Hadoop when scheduling map tasks but bypassed when scheduling reduce tasks.
-MapReduce is aware of the network locations of splits (inputstomappers)andleveragessuchinformationtoschedule mappers nearby splits.
-In contrast, MapReduce is oblivious to the network locations of partitions (inputs to reducers) and does not schedule reducers nearby partitions.
-Thus, similar to map task scheduling, we suggest making MapReduce aware of partitions network locations in order to apply locality to reduce task scheduling
-
-As we will be able to explain later, this design allows us to exploit data locality to increase system performance; in fact, when
-
-From an implementation point of view, we used services offered by Apache ZooKeeper to implement our leader election mechanism.
-
- by a set of distributed processes:
-
-\begin{description}
-\item[Client Process] the clients that request the execution of jobs composed by map and reduce tasks
-
-\item[Leader Primary Process] It manages the execution of word-count jobs received from clients coordinating Worker Nodes
-
-\item[Backup Primary Process] It manages the execution of word-count jobs received from clients coordinating Worker Nodes
-
-\item[Worker Process] A Worker Process executes map and reduce task scheduleted by current Leader Primary Process.
-In order to achieve fault tolerance, any Worker Process must be run indepently on different host.
-In our implementation, each process run on independent Amazon EC2 server
-
-The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover.
-This helps the Mesos master scale to large clusters with many tasks and frameworks.
-A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.
-
-\item[Worker Group] All system's nodes in which worker process are running are logically split into several \textit{Groups}, that is sets of equal worker processes, each of which execute the same commands using same input data in the same order.
-In a group all worker processes run independently on different host and they do not interact with each other in any way.
-Current Leader Primary Process can interact with groups members using a push-based approach in order to schedule map or reduce tasks.
-Although, for performance reasons, not always happen, when a task is sent to the group itself, all members of the group receive it.
-
-The key property that all groups have is that when a
-message is sent to the group itself, all members of the group receive it.
-
- primary coordinates all write
-operations
-
- In other words, we can replicate processes and organize them into a group to replace a single (vulnerable) process with a (fault tolerant) group.
-
- When a task is  for work is generated, either
-by an external client or by one of the workers, it is sent to the coordinator.
-
-as  a set of Task- Trackers that execute tasks
-\end{description}
-
-\subsection{The algorithm}
-
-In order to achieve 
-A simplistic solution to make MapReduce
-Byzantine fault-tolerant given the system model would be the
-following. First, the JobTracker starts 2f + 1 replicas of each
-map task in different servers and TaskTrackers. Second, the
-JobTracker starts also 2f + 1 replicas of each reduce task.
-Each reduce task fetches the output from all map replicas,
-picks the most voted results, processes them and stores its
-output in HDFS. In the end, either the client or a special task
-must make the vote of the outputs to pick the most voted. An
-even more simplistic solution would be to run a consensus,
-or Byzantine agreement between each set of map task repli-
-cas and reduce task replicas. This would involve even more
-replicas (typically 3f + 1) and more messages exchanged.
-
-\subsection{Crash failure detection}
-
-\subsection{Deferred execution} As known, arbitrary faults are very hard to detect and manage
-
-Deferred execution. Crash faults are detected by the previ-
-ously existing Hadoop mechanisms, and arbitrary faults are
-uncommon, so there is no point in always executing $2f + 1$ replicas to usually obtain the same result.
-
-By default, current leader primary process starts only $f + 1$ replicas of the same task, then wait results checking if they all return the same result.
-If a timeout elapses, or some returned results do not match, more replicas (up to $f$) are started, until there are $f + 1$ matching replies.
-
-In the best case, without Byzantine faults, only f + 1 replicas are started. If arbitrary faults are uncommon, we have a < f + 1 replica started reducing the overhead
-
-\section{Arbitrary Fault-Tolerant Locality-Aware MapReduce}
-
-\subsection{Arbitrary fault tolerance}
-
-As known academic literature describes many type of failure, like \textit{crash failures}; however the most serious are known as \textit{arbitrary failures} or \textit{Byzantine failures}, according to which a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.
-
-Redundancy represents the key technique used to manage these kind of failure, according to which,
-
-The key approach to tolerating a faulty process is to organize several identical processes into a group.
-
- Our BFT
-MapReduce follows the approach of executing each task more
-than once, similarly to the works mentioned above. The chal-
-
-Process groups are part of the solution for building fault-tolerant systems.
-In particular, having a group of identical processes allows us to mask one
-or more faulty processes in that group. In other words, we can replicate
-processes and organize them into a group to replace a single (vulnerable)
-process with a (fault tolerant) group.
-
-An important issue with using process groups to tolerate faults is how
-much replication is needed. To simplify our discussion, let us consider
-only replicated-write systems. A system is said to be k-fault tolerant if it
-can survive faults in k components and still meet its specifications. If the
-components, say processes, fail silently, then having k + 1 of them is enough
-to provide k-fault tolerance. If k of them simply stop, then the answer from
-the other one can be used.
-
-On the other hand, if processes exhibit arbitrary failures, continuing to
-run when faulty and sending out erroneous or random replies, a minimum
-of 2k + 1 processes are needed to achieve k-fault tolerance. In the worst case,
-the k failing processes could accidentally (or even intentionally) generate the
-same reply. However, the remaining k + 1 will also produce the same answer,
-so the client or voter can just believe the majority.
-
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{Bibliography}
 

### 2019-09-03 Paper.tex
update

@@
 
-Therefore we have adopted a design capable to reduce
+Therefore we have adopted a design aware of data locations and sizes capable to reduce the overall amount of transferred data; that solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}"; in other words  "\textit{moving computation towards data is cheaper than moving data towards computation}".
 
-Since moving data repeatedly among server is bottleneck, especially when large data set are involved, in order to improve system performance, we have adopt a design aware of data locations and sizes in order to mitigate network traffic avoiding pointless data moving.
+To be more precise, when a WP complete a map task, it send as output to LPP two very important information: a string containing data output digest and a value representing output data size.
+According to Hadoop terminology, map task output are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one?
 
-Our solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}".
-When the map phase is fully done, all the network locations of the feeding nodes of every reducer will be known
+Assume for simplicity that no faults occurs and to have only two WPGs $\lbrace g_1, g_2 \rbrace$.
+Let $P_{i:g_i}$ the partition owned by WPG $g_i$ which contains all key-value pairs which must be submitted to reduce task $R_i$.
+The problem is how to perform a locality-aware reduce task scheduling; in other word, which WPG $g_i$ have to run reduce task $R_i$ reducing shuffled data?
 
-Moving data repeatedly to distant nodes is becoming the bottleneck [23].
-In this paper we rethink reduce task scheduling in Hadoop and suggest making Hadoop’s reduce task scheduler aware of partitions’ network locations and sizes in order to mitigate network traffic.
-
-A key question is how to schedule reduce tasks at Task Trackers so as to diminish shuffled data and improve MapReduce performance.
-One of Hadoop’s basic principles is: moving computation towards data is cheaper than moving data towards computation.
-Such a principle is employed by Hadoop when scheduling map tasks but bypassed when scheduling reduce tasks.
-MapReduce is aware of the network locations of splits (inputstomappers)andleveragessuchinformationtoschedule mappers nearby splits.
-In contrast, MapReduce is oblivious to the network locations of partitions (inputs to reducers) and does not schedule reducers nearby partitions.
-Thus, similar to map task scheduling, we suggest making MapReduce aware of partitions network locations in order to apply locality to reduce task scheduling
+Suppose that $P_{1:g_1}$, $P_{2:g_1}$, $P_{1:g_2}$ and $P_{2:g_2}$ have a size of 300 MB, 150 MB, 150 MB and 300 MB respectively.
+Clearly, scheduling $R_1$ at $g_1$ and $R_2$ at $g_2$ reduce the amount of transferred data among WPGs by 50\%.
+Obliviously using this approach is possible to perform a locality-aware shuffle task capable to reduce network traffic, applying locality to reduce task scheduling.
 

### 2019-09-05 Paper.tex
update

@@
 \documentclass[sigchi]{acmart}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
 
-\subsection{Crash failure detection} To manage and detect workers processes crash faults we have use some features of Apache Zookeeper.
+\section{Implementation}
 
-As known, Apache ZooKeeper has the notion of \textit{ephemeral nodes}, that is special znodes which exists as long as the \textit{session} that created the znode is active.
+In this last section we will describe some main aspect of our implementation.
+
+\subsection{Crash failure detection} To guarantee the correct functioning of the system, is critical to be able to detect WP and PP crash failure.
+To resolve this problem we have exploited some features of Apache Zookeeper.
+
+As known, Apache ZooKeeper has the notion of \textit{ephemeral nodes}, special znodes which exists as long as the \textit{session} that created the znode is active.
 When session expiration occurs, Zookeeper cluster will delete all ephemeral nodes owned by that session and immediately notify all connected clients of the change.
@@
 
-Notice that session is kept alive by requests sent by client, therefore is critical that client will send PING request to keep the session alive.
-This PING request not only allows the ZooKeeper server to know that the client is still active, but it also allows the client to verify that its connection to the ZooKeeper server is still active.
+Therefore using that feature, we adopted a very simple design according to which any process must to "sign up" creating his own ephemeral node in Zookeeper Cluster in known paths (note that znode paths of PPs and WPs are different in order to not interfere with leader election of PPs).
 
-Using this design, is very easy to keep check the status of worker processes.
+It will be the responsibility of LPP to watch for WP's ephemeral node deletions; this approach makes WP status checking very simple.
+System coordination and membership is facilitated too, since any ephemeral node is used to store information about process that created (ID, Group ID etc.).
+
+\subsection{Primary process leader election algorithm}
+
+\begin{algorithm}
+\caption{}\label{alg:leaderElection}
+\begin{enumerate}
+
+\item Let \texttt{ROOT} be a valid znode path.
+Any PP, which wants to become leader, creates a new znode $Z$ with path \texttt{ROOT/$x$}, where $x$ is a number.
+Using both \texttt{SEQUENCE} and \texttt{EPHEMERAL} flags, $x$ will be the sequence number greater than any one previously used.
+
+\item Let $C$ be the children of \texttt{ROOT}.
+
+\item If $Z$ is the smallest node in $C$, that is $x$ is the smallest sequence number used so far, then the PP that created $Z$ will become leader.
+
+\begin{enumerate}
+
+\item Otherwise watch for changes on znode \texttt{ROOT/$j$} in C, where $j$ is the largest sequence number such that $j$ < $x$.
+
+\item Upon receiving a notification of znode deletion, go to step number 2.
+
+\end{enumerate}
+\end{enumerate}
+\end{algorithm}
+
+Let's now describe in details how we have resolved leader election problem of a PP using Apache Zookeeper.
+
+Suppose that \texttt{ROOT} is a valid path of an existing znode.
+To apply as possible leader, any PP creates a znode child into \texttt{ROOT} using \texttt{SEQUENCE} and \texttt{EPHEMERAL} flags.
+When \texttt{SEQUENCE} is used, ZooKeeper cluster automatically appends a sequence number to the new znode that is greater than any one previously appended to a child of \texttt{ROOT}.
+The PP, which created the znode with the smallest appended sequence number, become leader.
+
+Obliviously is important to watch for failures of the leader in a such way that a new PP arises as the new leader when leader fails.
+Note that, since we have used \texttt{EPHEMERAL} flag during znode creation, when leader fails the smallest znode will be deleted by Zookeeper cluster.
+if we make sure that all PPs watch for the next znode down on the sequence of znodes, if a PP receives a notification that the znode it is watching is gone, then it becomes the new leader since there is no smaller znode.
+
+A complete description of leader election algorithm is shown in Algorithm \ref{alg:leaderElection} while our implementation is in \texttt{SDCC-Project/aftmapreduce/cloud/zookeeper}
 

### 2019-09-07 Paper.tex
update

@@
 Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on different machines; using any leader election algorithm, is possible to elect one of these copies as \textit{Leader Primary Process} (LPP) while all the others remain on stand-by.
-Using this approach, is possible to manage PP crash failure: when current leader fails, a backup copy is promoted to become the new .
+Using this approach, is possible to manage PP crash failure: when current leader fails, a backup copy is promoted to become the new leader.
 
@@
 
+\section{The algorithm}
+
+In this section we will provide a detailed description of our MapReduce algorithm used to fully accomplish any client's word-count request.
+Our algorithm is made up of five phases every of which have to be successfully completed in order to complete a request.
+
+\subsection{Acceptance phase}
+
+In this initial phase, client queries Zookeeper cluster in order to know who current LPP is by requiring its public internet address.
+
+Then, client send his request directly to LPP including text input data through a RPC call.
+Then, received text input data is written into a DFS (\textit{Distributed File System)} or, equivalently, into an external storage service (in our prototype, we have adopted Amazon S3), while several client request's meta-data (request's status information, text input data digest etc.) are stored into Zookeeper cluster by LPP.
+
+Finally, LPP notifies client that his request is been accepted by system; then the client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
+
+If any error occurs during this phase, client would have to re-forward its request until it will receive acceptance confirmation.
+Note that we have adopted a \textit{most-once semantics} to manage duplicated requests; in fact, LPP is able to recognize duplicates re-forward its reply to the client.
+
+\subsection{Map phase}
+
+LPP splits received text into $n$ splits where $n$ is the number of WPGs currently available in the cluster (this number is checked at runtime).
+Then LPP starts \textit{Map Phase} during which $n$ \textit{Arbitrary-Fault-Tolerant Map Tasks} (AFT-MTs) are initialized and assigned to every WPGs (note that each WPG manages a different AFT-MT).
+
+To make this phase fault tolerant, each AFT-MT is replicated using the WPs available into a WPG specified by LPP.
+As explain in previous sections deferred execution and digest outputs are used.
+Our prototype is designed to check at runtime the number of currently available WPs into a WPG calculating automatically fault tolerance level (for example if there are three WP currently on-line of a specified group, the system behaves properly in order to tolerate one arbitrary failure).
+
+When all AFT-MTs finish successfully, LPP perform a checkpoint storing into Zookeeper cluster a set of meta-data used to restore LPP status in case of crash (these data include digest outputs from WPGs and some information about computed data outputs owned by WPGs).
+
+In case of LPP crash (also an high amount of arbitrary fails of WPs determines a LPP crash), after using our leader election algorithm, a PP backup copy becomes leader.
+Then the new leader recovers previous leader's status from last checkpoint querying Zookeeper cluster.
+All pending requests are restarted according to last checkpoint while input text data are retrieved, if necessary, from DFS or an equivalent storage service.
+
 \section{Implementation}

### 2019-09-08 Paper.tex
update

@@
 
+\subsection{Data upload phase}
+
+The first phase of our algorithm expects that client would upload their test input file into a DFS (\textit{Distributed File System)} or, equivalently, into an external storage service.
+
+Although the simplicity of this algorithm's phase, there are some very important consideration about our prototype.
+Unlike Hadoop which use HDFS (\textit{Hadoop Distributed File System}) to store clients input data, our implementation adopts a cloud storage service called Amazon S3.
+However, according to Amazon S3 implementation, since all objects and directories (called \textit{buckets}), by default, are private, clients cannot upload or download data without AWS security credentials or permissions.
+
+Therefore, in order to able clients to upload input data into Amazon S3, we have adopted a design based on \textit{pre-signed URLs}.
+According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can then upload (or download) an object.
+However only someone that has a valid security credentials can create a pre-signed URL.
+
+Therefore, in order to successfully upload an object, clients must obtain a pre-signed URL asking to LPP, which  have necessary privileges for pre-signed URL creation\footnote{To give all privileges required for pre-signed URL creation to our EC2 instances, where LPP are running, we have properly set the IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}.
+
+So, to get a pre-signed URL, clients query Zookeeper cluster in order to know who is the current LPP by requiring its public internet address.
+Then, client sends a request to LPP in order to obtain a pre-signed URL through which input text file will been uploaded.
+
 \subsection{Acceptance phase}
 
-In this initial phase, client queries Zookeeper cluster in order to know who current LPP is by requiring its public internet address.
+After data upload, client send a request to current LPP.
 
-Then, client send his request directly to LPP including text input data through a RPC call.
-Then, received text input data is written into a DFS (\textit{Distributed File System)} or, equivalently, into an external storage service (in our prototype, we have adopted Amazon S3), while several client request's meta-data (request's status information, text input data digest etc.) are stored into Zookeeper cluster by LPP.
+As soon as LPP receives a client's request, it starts to write several request's meta-data (request's status information, text input data digest etc.) into Zookeeper cluster.
+Finally, LPP notifies client that his request is been accepted by system.
+Then, client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
 
-Finally, LPP notifies client that his request is been accepted by system; then the client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
-
-If any error occurs during this phase, client would have to re-forward its request until it will receive acceptance confirmation.
+If any error occurs during this phase, client would have to re-forward its request to LPP until it will receive acceptance confirmation.
 Note that we have adopted a \textit{most-once semantics} to manage duplicated requests; in fact, LPP is able to recognize duplicates re-forward its reply to the client.
+If LPP crashes, client queries Zookeeper cluster in order to know who is the new LPP.
 
@@
 
-In case of LPP crash (also an high amount of arbitrary fails of WPs determines a LPP crash), after using our leader election algorithm, a PP backup copy becomes leader.
+In case of LPP crash (note that also an high amount of arbitrary fails of WPs determines a LPP crash), after using our leader election algorithm, a PP backup copy becomes leader.
 Then the new leader recovers previous leader's status from last checkpoint querying Zookeeper cluster.
 All pending requests are restarted according to last checkpoint while input text data are retrieved, if necessary, from DFS or an equivalent storage service.
+
+\subsection{Locality-aware shuffle and reduce phase}
 

### 2019-09-08 Paper.tex
update

@@
 
-\section{The algorithm}
+\section{System features}
 
@@
 Obliviously using this approach is possible to perform a locality-aware shuffle task capable to reduce network traffic, applying locality to reduce task scheduling.
-
-\section{The algorithm}
-
-In this section we will provide a detailed description of our MapReduce algorithm used to fully accomplish any client's word-count request.
-Our algorithm is made up of five phases every of which have to be successfully completed in order to complete a request.
-
-\subsection{Data upload phase}
-
-The first phase of our algorithm expects that client would upload their test input file into a DFS (\textit{Distributed File System)} or, equivalently, into an external storage service.
-
-Although the simplicity of this algorithm's phase, there are some very important consideration about our prototype.
-Unlike Hadoop which use HDFS (\textit{Hadoop Distributed File System}) to store clients input data, our implementation adopts a cloud storage service called Amazon S3.
-However, according to Amazon S3 implementation, since all objects and directories (called \textit{buckets}), by default, are private, clients cannot upload or download data without AWS security credentials or permissions.
-
-Therefore, in order to able clients to upload input data into Amazon S3, we have adopted a design based on \textit{pre-signed URLs}.
-According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can then upload (or download) an object.
-However only someone that has a valid security credentials can create a pre-signed URL.
-
-Therefore, in order to successfully upload an object, clients must obtain a pre-signed URL asking to LPP, which  have necessary privileges for pre-signed URL creation\footnote{To give all privileges required for pre-signed URL creation to our EC2 instances, where LPP are running, we have properly set the IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}.
-
-So, to get a pre-signed URL, clients query Zookeeper cluster in order to know who is the current LPP by requiring its public internet address.
-Then, client sends a request to LPP in order to obtain a pre-signed URL through which input text file will been uploaded.
-
-\subsection{Acceptance phase}
-
-After data upload, client send a request to current LPP.
-
-As soon as LPP receives a client's request, it starts to write several request's meta-data (request's status information, text input data digest etc.) into Zookeeper cluster.
-Finally, LPP notifies client that his request is been accepted by system.
-Then, client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
-
-If any error occurs during this phase, client would have to re-forward its request to LPP until it will receive acceptance confirmation.
-Note that we have adopted a \textit{most-once semantics} to manage duplicated requests; in fact, LPP is able to recognize duplicates re-forward its reply to the client.
-If LPP crashes, client queries Zookeeper cluster in order to know who is the new LPP.
-
-\subsection{Map phase}
-
-LPP splits received text into $n$ splits where $n$ is the number of WPGs currently available in the cluster (this number is checked at runtime).
-Then LPP starts \textit{Map Phase} during which $n$ \textit{Arbitrary-Fault-Tolerant Map Tasks} (AFT-MTs) are initialized and assigned to every WPGs (note that each WPG manages a different AFT-MT).
-
-To make this phase fault tolerant, each AFT-MT is replicated using the WPs available into a WPG specified by LPP.
-As explain in previous sections deferred execution and digest outputs are used.
-Our prototype is designed to check at runtime the number of currently available WPs into a WPG calculating automatically fault tolerance level (for example if there are three WP currently on-line of a specified group, the system behaves properly in order to tolerate one arbitrary failure).
-
-When all AFT-MTs finish successfully, LPP perform a checkpoint storing into Zookeeper cluster a set of meta-data used to restore LPP status in case of crash (these data include digest outputs from WPGs and some information about computed data outputs owned by WPGs).
-
-In case of LPP crash (note that also an high amount of arbitrary fails of WPs determines a LPP crash), after using our leader election algorithm, a PP backup copy becomes leader.
-Then the new leader recovers previous leader's status from last checkpoint querying Zookeeper cluster.
-All pending requests are restarted according to last checkpoint while input text data are retrieved, if necessary, from DFS or an equivalent storage service.
-
-\subsection{Locality-aware shuffle and reduce phase}
-
-\section{Implementation}
-
-In this last section we will describe some main aspect of our implementation.
 
@@
 
+\section{The algorithm}
+
+In this section we will provide a detailed description of our MapReduce algorithm used to fully accomplish any client's word-count request.
+Our algorithm is made up of five phases every of which have to be successfully completed in order to complete a request.
+
+\subsection{Data upload phase}
+
+The first phase of our algorithm expects that client would upload their test input file into a DFS (\textit{Distributed File System)} or, equivalently, into an external storage service.
+
+Although the simplicity of this algorithm's phase, there are some very important consideration about our prototype.
+Unlike Hadoop which use HDFS (\textit{Hadoop Distributed File System}) to store clients input data, our implementation adopts a cloud storage service called Amazon S3.
+However, according to Amazon S3 implementation, since all objects and directories (called \textit{buckets}), by default, are private, clients cannot upload or download data without AWS security credentials or permissions.
+
+Therefore, in order to able clients to upload input data into Amazon S3, we have adopted a design based on \textit{pre-signed URLs}.
+According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can then upload (or download) an object.
+However only someone that has a valid security credentials can create a pre-signed URL.
+
+Therefore, in order to successfully upload an object, clients must obtain a pre-signed URL asking to LPP, which  have necessary privileges for pre-signed URL creation\footnote{To give all privileges required for pre-signed URL creation to our EC2 instances, where LPP are running, we have properly set the IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}.
+
+So, to get a pre-signed URL, clients query Zookeeper cluster in order to know who is the current LPP by requiring its public internet address.
+Then, client sends a request to LPP in order to obtain a pre-signed URL through which input text file will been uploaded.
+
+\subsection{Acceptance phase}
+
+After data upload, client send a request to current LPP.
+
+As soon as LPP receives a client's request, it starts to write several request's meta-data (request's status information, text input data digest etc.) into Zookeeper cluster.
+Finally, LPP notifies client that his request is been accepted by system.
+Then, client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
+
+If any error occurs during this phase, client would have to re-forward its request to LPP until it will receive acceptance confirmation.
+Note that we have adopted a \textit{most-once semantics} to manage duplicated requests; in fact, LPP is able to recognize duplicates re-forward its reply to the client.
+If LPP crashes, client queries Zookeeper cluster in order to know who is the new LPP.
+
+\subsection{Map phase}
+
+LPP splits received text into $n$ splits where $n$ is the number of WPGs currently available in the cluster (this number is checked at runtime).
+Then LPP starts \textit{Map Phase} during which $n$ \textit{Arbitrary-Fault-Tolerant Map Tasks} (AFT-MTs) are initialized and assigned to every WPGs (note that each WPG manages a different AFT-MT).
+
+To make this phase fault tolerant, each AFT-MT is replicated using the WPs available into a WPG specified by LPP.
+As explain in previous sections deferred execution and digest outputs are used.
+Our prototype is designed to check at runtime the number of currently available WPs into a WPG calculating automatically fault tolerance level (for example if there are three WP currently on-line of a specified group, the system behaves properly in order to tolerate one arbitrary failure).
+
+When all AFT-MTs finish successfully, LPP perform a checkpoint storing into Zookeeper cluster a set of meta-data used to restore LPP status in case of crash (these data include digest outputs from WPGs and some information about computed data outputs owned by WPGs).
+
+In case of LPP crash (note that also an high amount of arbitrary fails of WPs determines a LPP crash), after using our leader election algorithm, a PP backup copy becomes leader.
+Then the new leader recovers previous leader's status from last checkpoint querying Zookeeper cluster.
+All pending requests are restarted according to last checkpoint while input text data are retrieved, if necessary, from DFS or an equivalent storage service.
+
+\subsection{Locality-aware shuffle and reduce phase}
+
+Any mapper send to LPP information about computed data like its size.
+Using all informations collected from each on-line WP during previous phase, LPP perform a locality-aware data shuffle according to which our system avoids transferring large partitions, shuffling smaller ones and saving network bandwidth.
+
+Since, according to our design, any WPG can receive a partition from any other, we need to wait until all mappers complete to certainly designate all the network locations of partitions.
+When map phase is fully done and all the network locations known, LPP starts to coordinates shuffle phase, ordering to some or all WGs to move part of their data to precisely location.
+These location are computed in order to shuffle smaller partition only.
+
+When shuffle phase is fully complete, LPP starts to coordinate $n$ Arbitrary-Fault-Tolerant Reduce Tasks (AFT-RTs) assigning them to every WPGs which now have all necessary data to perform this kind of operation.
+When all AFT-RTs fully finish, LPP perform another checkpoint in order to restore from an eventual LLP's crash.
+
+If too many arbitrary errors occur, making AFT-RTs completion impossible, it's enough to restart current phase.
+
+\subsection{Retrieve and Collect phase}
+
+When reducer phase is fully done, LPP start to retrieve all reduce outputs from WPs.
+To be more precise, for every available WPG in system LPP picks a single WP which, according to data received during last phase, has computed correct outputs.
+
+Then all reduce outputs are finally concatenated in an single output file by LPP which store these data into Zookeeper Cluster.
+LPP informs the client which can retrieve his output from Zookeeper cluster.
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-09-10 Paper.tex
update

@@
 
-After data upload, client send a request to current LPP.
+After data upload, client sends a word-count request to current LPP.
 
-As soon as LPP receives a client's request, it starts to write several request's meta-data (request's status information, text input data digest etc.) into Zookeeper cluster.
-Finally, LPP notifies client that his request is been accepted by system.
-Then, client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
+When that request is been received, LPP, after to have written into Zookeeper cluster all necessary information  in order restore its state after a crash failure (request's status information, text input data digest etc.),  notifies client that his request is been accepted by system, starting Map phase.
 
-If any error occurs during this phase, client would have to re-forward its request to LPP until it will receive acceptance confirmation.
-Note that we have adopted a \textit{most-once semantics} to manage duplicated requests; in fact, LPP is able to recognize duplicates re-forward its reply to the client.
-If LPP crashes, client queries Zookeeper cluster in order to know who is the new LPP.
+When LPP response is been received, client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
+
+If any error occurs during this phase, client have to re-forward its request to LPP until it will receive acceptance confirmation.
+
+Note that our system is able to manage duplicated requests because we have adopted a \textit{most-once semantics}; in fact, LPP is able to recognize duplicates re-forwarding its reply to client while client, if it detects that LPP is been crashed, forwards a query to Zookeeper cluster in order to know who is the new LPP.
 
@@
 
-Then all reduce outputs are finally concatenated in an single output file by LPP which store these data into Zookeeper Cluster.
-LPP informs the client which can retrieve his output from Zookeeper cluster.
+Then all reduce outputs are finally concatenated in an single output file.
+LPP stores output file into Amazon S3 using its digest as key.
+Then LPP informs the client sending output file digest through which client can retrieve his output.
 

### 2019-09-12 Paper.tex
URRAAAA

@@
 
-Various data-intensive tasks, like seismic simulation, natural language processing, machine learning, astronomical data parsing, web data mining and many other, require a processing power that exceeds the capabilities of individual computers imposing the use of a \textit{distributed computing} \cite{LARTS}.
+Various data-intensive tasks, like seismic simulation, natural language processing, machine learning, astronomical data parsing, web data mining and many others, require a processing power that exceeds the capabilities of individual computers imposing the use of a \textit{distributed computing} \cite{LARTS}.
 
@@
 A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{DRAMError}.
-A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent.
-\cite{MicrosoftStudyFailure} Moreover moving large amount of data repeatedly to distant nodes is becoming the bottleneck owing to an increased network traffic causing performance degradation.
+A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent \cite{MicrosoftStudyFailure}.
+Moreover moving large amount of data repeatedly among distant nodes is becoming the bottleneck owing to an increased network traffic, causing significant performance degradation.
 
-Therefore to construct a distributed system capable to provide its services even in the presence of failures is become so critical; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.
+Therefore to construct a distributed system capable to provide its services even in the presence of failures, that is to design a \textit{fault tolerant} cloud application, is a critical aspect of software engineering.
 
-Moreover, due to very large data-set involved during data-intensive tasks, exploiting data locality, in order to mitigate network traffic and delay, becomes very important to improve performance.
+Moreover, due to very large data-set involved during data-intensive tasks, exploiting data locality becomes crucial aspect in order to mitigate network traffic and delay, improving so performance.
 
-In these paper we will describe our \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system capable to resolve all issues described above.
-We have implemented an AFTLA MapReduce system, capable to perform a word-count of a given text input, from scratch using Go programming language, adopting Apache ZooKeeper\textsuperscript{TM} for maintaining configuration information and system coordination \footnote{See \url{https://zookeeper.apache.org}}; all libraries used in our implementation are fully described in table \ref{tab:libraries}.
-Our prototype    's source code is fully available on GitHub\footnote{See \url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.
+In these paper we will describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system which is capable to resolve all issues described above.
+
+Our AFTLA MapReduce prototype, which is capable to perform a word-count by a given text input file, is been implemented from scratch using Go programming language using some external libraries, including those necessary to interact with an Apache ZooKeeper\textsuperscript{TM} cluster\footnote{\url{https://zookeeper.apache.org}}, which we have adopt for system's coordination purposes, and with Amazon AWS services, because we have adopt Amazon S3 for storage; note that all libraries used in our prototype are fully described in table \ref{tab:libraries}.
+
+Our prototype is been design to run into several Amazon EC2 instances hosted in a same region (\texttt{us-east-1})\footnote{Note that, due to Account AWS Educate Starter limitations, we could not run Amazon EC2 instances on other regions.}, adopting AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} to associate some of our EC2 instance to an public IPv4 address in order to enable communication with the internet and then to connect a local computer to our system.
+
+Finally, we remember that our prototype's source code is fully available on GitHub\footnote{\url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.
 
@@
 
-Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center; in our prototype, every process run on his own Amazon EC2 server hosted in a same region (\texttt{us-east-1}).
-All processes interact with each other using RPC
+Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center.
 
@@
 All processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by TCP connections.
-All system processes use RPC protocol in order to interact with each other.
+In our prototype, all system's processes use RPC protocol in order to interact with each other.
 
@@
 
-In this paper, we take for granted reader's knowledge of the MapReduce framework and Hadoop implementation. framework.
+In this paper, we take for granted reader's knowledge of the MapReduce framework and main aspects of Hadoop  framework.
 
@@
   \caption{System Architecture}
+  \label{fig:model}
 \end{figure}
 
-Three kind of process are used in our system:
+As you can see from figure \ref{fig:model}, three kind of process exist in our system:
 
 \begin{description}
-\item[Client Processes] Which send word-count requests to our system sending directly an input text file.
+\item[Client Processes] Which sends (word-count) requests to our system.
 
-\item[Worker Process (WP)] They execute \textit{map} or \textit{reduce} scheduled by LPP.
+\item[Worker Process (WP)] They execute \textit{map} or \textit{reduce} tasks scheduled by system's leader.
 
-\item[Primary Process (PP)] It is similar to \textit{JobTracker} process used in Apache Hadoop which duty is to satisfy clients requests scheduling \textit{map} or \textit{reduce} tasks. 
+\item[Primary Process (PP)] It is similar to \textit{JobTracker} process used in Apache Hadoop which duty is to satisfy clients requests scheduling \textit{map} or \textit{reduce} tasks to WPs, coordinating all system.
 \end{description}
@@
 
-Unlike Hadoop, according to which \textit{JobTracker} process is assumed always correct, the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents a \textit{single point of failure}.
+Unlike Hadoop, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}.
 
-Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on different machines; using any leader election algorithm, is possible to elect one of these copies as \textit{Leader Primary Process} (LPP) while all the others remain on stand-by.
-Using this approach, is possible to manage PP crash failure: when current leader fails, a backup copy is promoted to become the new leader.
+Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by.
+Using this approach, is possible to manage PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.
 
-LPP represents our system coordinator since only it can can interact with WP scheduling task using a \textit{push-based} approach (unlike Hadoop according to which JobTracker schedules task using a \textit{pull-based} approach \cite{LARTS})
+, only LPP can interact with WPs and modify data into the Zookeeper Cluster.
+Note that LPP schedules several task using a \textit{push-based} approach (unlike Hadoop according to which JobTracker schedules task using a \textit{pull-based} approach \cite{LARTS})
 

### 2019-09-19 Paper.tex
dsadsadas

@@
 
+As you can see from figure \ref{fig:model}, our system is made up of several kinds of processes each of which has its own features and purposes.
+
 \begin{figure}[h]
   \centering
-  \includegraphics[width=\linewidth]{Architecture}
+  \includegraphics[width=\linewidth]{Architecture.png}
   \caption{System Architecture}
@@
 
-As you can see from figure \ref{fig:model}, three kind of process exist in our system:
+\subsection{Client Process}
 
-\begin{description}
-\item[Client Processes] Which sends (word-count) requests to our system.
+This process, which, as said previously, is assumed always correct, is the place where (word-count) jobs are submitted to our system.
 
-\item[Worker Process (WP)] They execute \textit{map} or \textit{reduce} tasks scheduled by system's leader.
+It can interact with system's key-value storage service (i.e.
+DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading using HTTP-based RESTful APIs, according to which both an URL and the use of standard HTTP methods (\texttt{GET} and \texttt{PUT}) only are required in order to perform data transmission between our cloud system and client
 
-\item[Primary Process (PP)] It is similar to \textit{JobTracker} process used in Apache Hadoop which duty is to satisfy clients requests scheduling \textit{map} or \textit{reduce} tasks to WPs, coordinating all system.
-\end{description}
+Is very important to specify that, in our system, URLs are provided by current leader primary process (CLPP) for security and compatibility reasons with some cloud storage services.
+In fact, unlike Hadoop, which use HDFS (\textit{Hadoop Distributed File System}) to store input and output data, our prototype adopts Amazon S3 for data storage purposes.
+According to Amazon S3 implementation, since all objects and directories (latter are called \textit{buckets}) are by default private, clients cannot upload or download data without AWS security credentials or permissions.
+
+Therefore, rather than distribute AWS security credentials which can imply huge security risks, we have adopt a design according to which client processes have to request special URLs to CLPP to accomplish their data transmissions; these kind of URLs are called \textit{pre-signed URLs}.
+According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can upload (or download) an object from Amazon S3.
+However only someone that has a valid security credentials can create a pre-signed URL; this is the reason according to which CLPP, which has AWS security credentials to interact with Amazon S3\footnote{We remember that to give all privileges required for pre-signed URL creation to the EC2 instances where CLPP are running, we have to properly set all necessary IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}, has to generate and distribute them to clients.
+
+However clients process are unaware of CLPP network location which, as we will see in the next paragraph, can change during system activities due to either a crash or connectivity lost.
+To be more precise any system's process know network location of the others although Zookeeper cluster location, which we have adopt for membership managing and coordination purposes, must be known by everyone; therefore we can state that location transparency of our application is only partial.
+
+Since, as we will see, is possible to know network location of a specified process querying Zookeeper cluster, clients are able to know where CLPP is both to require pre-signed URL and to submit jobs.
 
@@
 
-\subsection{Deferred execution} We believe that there is no point in always executing $2f + 1$ replicas for each task to usually obtain the same result.
+\subsection{Locality-Aware Deferred Execution}
 
-To minimize both the number of copies of tasks executed and the overhead due to network traffic we have adopted a design called \textit{deferred execution}: according to that solution current LPP starts only $f + 1$ replicas of the same task, checking if they all return the same result.
-If a time-out elapses, or some returned results do not match, more replicas (up to $f$) are started, until there are $f + 1$ matching replies.
+Waiting for $2f + 1$ matching replies during a AFT Map-Task can be a waste of time especially when no faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ Map-Task for each AFT Map-Task.
 
-We believe that this this design is also energy-saver and cost-effective since, supposing that arbitrary faults are uncommon, fewer WP are involved into computations respect to basic scheme and, in principle, is possible to start and use a fewer number of servers using auto-scaling techniques (at cost of some latency).
+Therefore, to minimize both the number of Map-Task executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware Deferred Execution}.
 
-\subsection{Data locality awareness}
+According to that solution, during a AFT Map-Task execution, only $f + 1$ Map-Task replicas are started checking if they all return the same result.
+If a time-out elapses or some return results do not match, more Map-Task replicas (up to $f$) are started, until we obtain $f + 1$ matching replies.
+When faults are unlikely, this approach, which we believe to be energy-saver\footnote{Assuming that idle WPs consume less energy respect to non-idle WPs, minimize the number of Map-Task executed involves minimize the amount of electricity used.}, is capable to minimize the number of WPs involved into computations respect to basic scheme, improving overall system performance.
+
+Moreover, this mechanism can reduce overall system response time because it is designed to minimize data transfer time too.
+When an AFT Map-Task starts $f + 1$ Map-Task replica on WPs, the latter are not chosen at random but according to their network location; in fact, Map-Task are scheduled firstly to the $f + 1$ nearest nodes giving priority to them.
+Only when we can't get $f + 1$ matching replies, the most distant nodes are used.
+The most difficult problem consists into determine WP's network location considering the variation of network traffic.
+In literature, many network proximity evaluation's methods exist which can be static (i.e.
+hop number) or dynamic (round-trip time evaluation, HTTP request emulation, etc.); in our prototype, we have adopt a very simple network proximity evaluation's method based on \texttt{ping} which able us to evaluate round-trip time among system's nodes.
+
+\subsection{Speculative Execution}
+
+Although the advantages of the locality-aware deferred execution mechanism, we believe that waiting for $f + 1$ matching Map-Task for every AFT Map-Task results before starting the Reduce-Phase can worsen the time for the job completion, especially when WPs arbitrary failures are uncommon.
+Formally, assuming that we have $n$ WPG, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies; all Map-Phase may require long time especially when network traffic or data set size are huge.
+
+A way to increase system's performance reducing its response time is the following: when all scheduled AFT Map-Tasks have received the \textit{first} Map-Task result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finish.
+Essentially, our system make a bet according to which arbitrary faults are highly unlikely therefore first Map-Task replies are considered as correct.
+This mechanism is called \textit{Speculative Execution}.
+
+Obviously validate the correctness of first Map-Task replies is critical otherwise job's output can be incorrect.
+In order to do that, all AFT Map-Tasks keep on waiting their $f + 1$ matching replies even when Reduce-Phase is started.
+When Map-Phase is fully finish, if is detected that the input used in the Reduce-Phase was not correct, Reduce-Phase will be restarted with the correct input, otherwise we can finish our job in much less time.
+
+Then, when there are no fault or they are unlikely, this design is capable to reduce considerably system's response time.
+
+\subsection{Data Locality-Aware Reduce Scheduling}
 
@@
 
-Although the simplicity of this algorithm's phase, there are some very important consideration about our prototype.
-Unlike Hadoop which use HDFS (\textit{Hadoop Distributed File System}) to store clients input data, our implementation adopts a cloud storage service called Amazon S3.
-However, according to Amazon S3 implementation, since all objects and directories (called \textit{buckets}), by default, are private, clients cannot upload or download data without AWS security credentials or permissions.
-
-Therefore, in order to able clients to upload input data into Amazon S3, we have adopted a design based on \textit{pre-signed URLs}.
-According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can then upload (or download) an object.
-However only someone that has a valid security credentials can create a pre-signed URL.
-
-Therefore, in order to successfully upload an object, clients must obtain a pre-signed URL asking to LPP, which  have necessary privileges for pre-signed URL creation\footnote{To give all privileges required for pre-signed URL creation to our EC2 instances, where LPP are running, we have properly set the IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}.
-
-So, to get a pre-signed URL, clients query Zookeeper cluster in order to know who is the current LPP by requiring its public internet address.
-Then, client sends a request to LPP in order to obtain a pre-signed URL through which input text file will been uploaded.
-
 \subsection{Acceptance phase}

### 2019-09-19 Paper.tex
dsadsadas

@@
 
-\keywords{MapReduce, Fault tolerance, Arbitrary failure, Data locality}
+\keywords{MapReduce, Arbitrary Fault Tolerance, Locality Awareness, Speculative Execution, Leader Election Algorithm, Deferred Execution}
 \maketitle
@@
 Finally, we remember that our prototype's source code is fully available on GitHub\footnote{\url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.
+In this paper, we take for granted reader's knowledge of the MapReduce framework and part of Hadoop framework.
 
@@
 
-In order to properly describe how our algorithm can tolerate arbitrary faults and to exploit data locality, it is necessary to describe its architecture.
-To do that, in this section we start making some very important assumptions.
+In order to properly describe how our system can achieve a certain level of arbitrary fault tolerance without unduly compromising performance, let's start making some very important assumptions.
 
-Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center.
+We have designed our cloud application as a \textit{set of processes}, every of which have to run on \textit{different} servers with a certain replication degree in order to achieve a certain level of arbitrary fault tolerance.
+Available processes are not all the same but several kind of these exist with its own features and aims which we will describe them in detail in following section; in fact, we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);
 
-We assume that our system runs \textit{asynchronously}, that is no assumptions about process execution speeds or message delivery times are made; therefore we can normally use timeouts to state that a process has crashed although, occasionally, such conclusion is false \cite{SDCC}.
+We assume that our system runs \textit{asynchronously}, that is no assumptions about process execution speeds or message delivery times are made; therefore we can normally use a time-out to state that a process has crashed although, occasionally, such conclusion is false \cite{SDCC}.
 
-All processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by TCP connections.
-In our prototype, all system's processes use RPC protocol in order to interact with each other.
+We assume that all processes are connected by \textit{reliable channels}, that is no messages are lost, duplicated or corrupted.
+In our prototype that feature is guaranteed  by the use of Go implementation of RPC\footnote{\url{https://golang.org/pkg/net/rpc/}} (\textit{Remote Procedure Call}) which is based on TCP connections.
+Mostly all RPC calls, except those made by the client process, are asynchronous\footnote{Although Go's \texttt{rpc} package provides its own support for RPC asynchronous calls, we have  preferred to adopt an equivalent approach based on properly used goroutine and channels.}.
 
@@
 Finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
-
-In this paper, we take for granted reader's knowledge of the MapReduce framework and main aspects of Hadoop  framework.
 
@@
 \subsection{Primary Process}
-At this point, is necessary to make some clarifications about PP's features.
 
-Unlike Hadoop, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}.
+Most of the activities carried out by a Primary Process (PP) are very similar to those performed by \textit{JobTracker} process used in Apache Hadoop framework.
+These activities including \textit{Map-Task} or \textit{Reduce-Task} scheduling, pre-signed URLs generation, managing of worker nodes replies, clients request managing and so on.
 
-Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by.
+However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}.
+Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by.
 Using this approach, is possible to manage PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.

### 2019-09-20 Paper.tex
dsadsadas

@@
 Both academic literature and daily experience shows that \textit{arbitrary faults} frequently occur corrupting our results \cite{BFLMapReduce}.
-Moreover, ignore data-set locality can lead to performance degradation and a pointless bigger network traffic \cite{LARTS}.
+Moreover, ignore \textit{data-set locality} can lead to performance degradation and a pointless bigger network traffic \cite{LARTS}.
 
-In this paper we present an original MapReduce runtime system capable both to tolerate arbitrary faults and to recognize input data network locations and sizes in order to perform a \textit{locality-aware task scheduling}, improving performance and diminishing network traffic.
-
-Although job's execution using our system requires more resources respect to other implementations, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
+In this paper we present a MapReduce runtime system as a solution to these problems.
+Although job's execution using our system requires more resources respect to other implementations due to process replications, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
 \end{abstract}
@@
 
-Therefore to construct a distributed system capable to provide its services even in the presence of failures, that is to design a \textit{fault tolerant} cloud application, is a critical aspect of software engineering.
+For these reasons, to construct a distributed system capable to provide its services even in the presence of failures, mitigating network traffic and delay, is become a critical aspect of software engineering.
 
-Moreover, due to very large data-set involved during data-intensive tasks, exploiting data locality becomes crucial aspect in order to mitigate network traffic and delay, improving so performance.
-
-In these paper we will describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system which is capable to resolve all issues described above.
-
-Our AFTLA MapReduce prototype, which is capable to perform a word-count by a given text input file, is been implemented from scratch using Go programming language using some external libraries, including those necessary to interact with an Apache ZooKeeper\textsuperscript{TM} cluster\footnote{\url{https://zookeeper.apache.org}}, which we have adopt for system's coordination purposes, and with Amazon AWS services, because we have adopt Amazon S3 for storage; note that all libraries used in our prototype are fully described in table \ref{tab:libraries}.
-
-Our prototype is been design to run into several Amazon EC2 instances hosted in a same region (\texttt{us-east-1})\footnote{Note that, due to Account AWS Educate Starter limitations, we could not run Amazon EC2 instances on other regions.}, adopting AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} to associate some of our EC2 instance to an public IPv4 address in order to enable communication with the internet and then to connect a local computer to our system.
-
-Finally, we remember that our prototype's source code is fully available on GitHub\footnote{\url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.
-In this paper, we take for granted reader's knowledge of the MapReduce framework and part of Hadoop framework.
+In these paper we will describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFT-LA) MapReduce system capable to resolve all issues described above.
 
@@
 
-\section{Assumptions}
+\section{Assumptions and remark}
 
-In order to properly describe how our system can achieve a certain level of arbitrary fault tolerance without unduly compromising performance, let's start making some very important assumptions.
+In order to properly describe how our system can achieve a certain level of arbitrary fault tolerance without unduly compromising performance, let's start making some very important assumptions and observations.
 
-We have designed our cloud application as a \textit{set of processes}, every of which have to run on \textit{different} servers with a certain replication degree in order to achieve a certain level of arbitrary fault tolerance.
-Available processes are not all the same but several kind of these exist with its own features and aims which we will describe them in detail in following section; in fact, we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);
+We have designed our cloud application as a \textit{set of processes}, every of which have to both run on \textit{different} servers and have got a certain replication degree in order to achieve a certain level of arbitrary fault tolerance, therefore we have deploy our processes in several Amazon EC2 instances hosted in a same region (\texttt{us-east-1})\footnote{Note that, due to Account AWS Educate Starter limitations, we couldn't run Amazon EC2 instances on other regions.}.
+
+In order to enable communication with the Internet and therefore allow a local computer to connect to our system, we have adopt AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} which able us to associate to some of our EC2 instance to a public static IPv4 addresses\footnote{Public IPv4 addresses associated to any EC2 instances by default change after every start.
+Therefore, if an Amazon EC2 crashed and have to be restarted, client wouldn't able to connect to it due to address change.}.
+
+Observe that processes are not all the same but several kind of these exist, with its own features and aims: although we will describe them in detail in following section, just note that we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);
+
+Note that our MapReduce system is been implemented to execute word-count job only.
+We have built our system from scratch using Go programming language\footnote{\url{https://golang.org}} using some external libraries, which are all reported in table \ref{tab:libraries}.
 
@@
 
-We assume that all processes are connected by \textit{reliable channels}, that is no messages are lost, duplicated or corrupted.
+All processes are connected by \textit{reliable channels}, that is no messages are lost, duplicated or corrupted.
 In our prototype that feature is guaranteed  by the use of Go implementation of RPC\footnote{\url{https://golang.org/pkg/net/rpc/}} (\textit{Remote Procedure Call}) which is based on TCP connections.
@@
 Clients are \textit{always correct}, because if they are not there is no point in worrying about the correctness of our system's output.
-Finally we assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
+We assume the existence of an hash function that is \textit{collisions-resistant}, for which it is infeasible to find two inputs that produce the same output.
+
+Finally, we remember that our prototype's source code is fully available on GitHub\footnote{\url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.
+In this paper, we take for granted reader's knowledge of the MapReduce framework and part of Hadoop framework.
 
@@
 
-As you can see from figure \ref{fig:model}, our system is made up of several kinds of processes each of which has its own features and purposes.
+Let's start now the analysis of all processes of our system.
 
@@
 It can interact with system's key-value storage service (i.e.
-DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading using HTTP-based RESTful APIs, according to which both an URL and the use of standard HTTP methods (\texttt{GET} and \texttt{PUT}) only are required in order to perform data transmission between our cloud system and client
+DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading.
+To perform data transmissions, client processes use HTTP-based RESTful APIs, according to which both an URL and standard HTTP methods (\texttt{GET} and \texttt{PUT}) only are required.
 
-Is very important to specify that, in our system, URLs are provided by current leader primary process (CLPP) for security and compatibility reasons with some cloud storage services.
+Is very important to specify that, in our system, URLs are provided by a PP for security and compatibility reasons with some cloud storage services.
 In fact, unlike Hadoop, which use HDFS (\textit{Hadoop Distributed File System}) to store input and output data, our prototype adopts Amazon S3 for data storage purposes.
-According to Amazon S3 implementation, since all objects and directories (latter are called \textit{buckets}) are by default private, clients cannot upload or download data without AWS security credentials or permissions.
+According to Amazon S3 implementation, since all objects and directories (\textit{buckets}) are by default private, clients cannot upload or download data without AWS security credentials or permissions.
 
-Therefore, rather than distribute AWS security credentials which can imply huge security risks, we have adopt a design according to which client processes have to request special URLs to CLPP to accomplish their data transmissions; these kind of URLs are called \textit{pre-signed URLs}.
+Therefore, rather than distribute AWS security credentials which can imply huge security risks, we have adopt a design according to which client processes have to request special URLs to PP to accomplish their data transmissions; these kind of URLs are called \textit{pre-signed URLs}.
 According to Amazon AWS documentation, anyone who receives a valid pre-signed URL can upload (or download) an object from Amazon S3.
-However only someone that has a valid security credentials can create a pre-signed URL; this is the reason according to which CLPP, which has AWS security credentials to interact with Amazon S3\footnote{We remember that to give all privileges required for pre-signed URL creation to the EC2 instances where CLPP are running, we have to properly set all necessary IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}, has to generate and distribute them to clients.
+However only someone that has a valid security credentials can create a pre-signed URL; this is the reason according to which PP, that has AWS security credentials to interact with Amazon S3\footnote{We remember that to give all privileges required for pre-signed URL creation to the EC2 instances where PP is running, we have to properly set all necessary IAM Roles thought "\textit{AWS Identity and Access Management service}" (IAM)}, has to generate and distribute them to clients.
 
-However clients process are unaware of CLPP network location which, as we will see in the next paragraph, can change during system activities due to either a crash or connectivity lost.
-To be more precise any system's process know network location of the others although Zookeeper cluster location, which we have adopt for membership managing and coordination purposes, must be known by everyone; therefore we can state that location transparency of our application is only partial.
-
-Since, as we will see, is possible to know network location of a specified process querying Zookeeper cluster, clients are able to know where CLPP is both to require pre-signed URL and to submit jobs.
+Observe that client processes are unaware of PP network location, that is they doesn't know its internet address (which can change during system activities due to either a crash or connectivity lost because to Amazon EC2 policies).
+To be more precise any system's process know network location of the others although an Apache Zookeeper\textsuperscript{TM}\ cluster location, which we have adopt for membership managing and coordination purposes, must be known by everyone.
+According to our design, is possible to know network location of a specified process querying Zookeeper cluster, therefore clients are able to know where PP is and then it can both require pre-signed URL and submit jobs.
 
@@
 
-Most of the activities carried out by a Primary Process (PP) are very similar to those performed by \textit{JobTracker} process used in Apache Hadoop framework.
+Most of the activities carried out by a Primary Process are very similar to those performed by \textit{JobTracker} process used in Apache Hadoop framework.
 These activities including \textit{Map-Task} or \textit{Reduce-Task} scheduling, pre-signed URLs generation, managing of worker nodes replies, clients request managing and so on.
@@
 Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by.
-Using this approach, is possible to manage PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.
-
-, only LPP can interact with WPs and modify data into the Zookeeper Cluster.
-Note that LPP schedules several task using a \textit{push-based} approach (unlike Hadoop according to which JobTracker schedules task using a \textit{pull-based} approach \cite{LARTS})
-
-However, to perform its task, LPP manages various information about clients requests, many of which, as we will see later, are sent by WP after a map or reduce task.
-In other word, LPP has got a status.
+Using this approach, is possible to manage a PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.
 
@@
 
-Therefore we have adopt a design according to which LPP make a sort of backup, or snapshot, of its current state regularly.
-To make our implementation easier, in our prototype, considering that LPP state contains a very small amount of data, LPP stores its state in a Zookeeper cluster after some events, like a map task termination.
-In case of crash failure of current LPP, when a primary process backup becomes leader, it retrieves all data from Apache ZooKeeper cluster, recovering last saved state.
+Therefore we have adopt a design according to which LPP save its state regularly.
+Since LPP state consists on a very small amount of data, we have design LPP to store its state into Apache Zookeeper cluster upon the occurrence of certain events.
+When a LPP crash failure occurs, the new leader can easily retrieves last saved state from  ZooKeeper cluster.
+Note that Apache Zookeeper's processes is been replicated too in order to tolerate a certain number of faults upon Zookeeper cluster.
+
+Another difference Hadoop \textit{JobTracker} process regards task scheduling approach.
+In our design LPP schedules tasks to WP using a \textit{push-based} approach, contrariwise Hadoop JobTracker schedules task using a \textit{pull-based} approach where WP ask for tasks\cite{LARTS}.
 
@@
 
-To make WP arbitrary fault-tolerant we have adopt a design according to which each task (map, reduce, etc.) is executed more than once by different processes running on different host.
-This approach requires to organize all our WPs into several \textit{groups} through which became possible to mask one or more faulty processes of a given group.
+To achieve fault tolerance we have adopt a design according to which each task is executed more than once by different processes running on different host.
+To do this, as you can see from figure \ref{fig:model}, we have adopt a design according to which all worker processes are organized in several groups which we have used to mask one or more faulty processes: these groups are called \textit{Worker Processes Group} (WPG).
+To be more precise, an WPG is a set of identical WP, each of which execute \textit{the same commands using the same input data in the same order}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.
 
-Before explaining how we manage WP faults, we must explain what is a Worker Processes Group (WPG).
-A WPG is a set of identical worker processes, each of which execute, relatively to a given job, \textit{the same commands using the same input data in the same order}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.
-All commands and data are sent by LPP.
+According to our system's design, any word-count job is made up of two main phases: \textit{Map-Phase} and \textit{Reduce-Phase}.
+To fully complete the Map-Phase of a job is necessary to successfully perform a certain number of special tasks called \textit{Arbitrary Fault-Tolerant Map-Tasks} (\textit{AFT-Map Tasks}): a AFT-Map represents a fault tolerant version of classical map task, in fact it simply consist on a replicated map task among a certain number of WP.
+To be more precise, our system is been design so that each WPG performs its own AFT-Map Task independently: to do that, each WPs, belonging to a given WPG, will perform the same map task in order to mask faulty processes.
+Clearly all this is also valid for Reduce-Phase.
 
-Suppose to want tolerate at most $f$ arbitrary failures of all WPs belonging to a given group.
-
-To achieve that level of fault-tolerance, we can apply to reach, for instance, \textit{byzantine agreement} among all processes belonging to group.
-However we believe that solution is too expensive because it requires, as properly explain in literature\citep{SDCC}, $3f + 1$ replicas.
+Suppose now to want tolerate at most $f$ arbitrary failures.
+To achieve that level of fault-tolerance is clearly necessary that any AFT-Map Task or AFT-Reduce Task assigned to each WPG are able to tolerate at most $f$ arbitrary failures.
+At this point we can apply, for instance, \textit{byzantine agreement} among all processes of a given WPG, but we believe that solution is too expensive because it requires, as properly explain in literature\citep{SDCC}, $3f + 1$ replicas.
 
@@
 
-In our design each map or reduce task scheduled by current LPP are assigned to independent WPGs.
-Let's try to explain this statement formally using map task as example (but is the same of any task).
-Let $i = 1,2,3...n$, where $n \in \mathbb{Z}_+$.
-As MapReduce framework states, our system splits the input text file $S$ in $n$ parts $\lbrace s_1, s_2, ...
-s_n \rbrace$ called \textit{split}; each split $s_i$ is associated to a map task $m_i \in \lbrace m_1, m_2, ...
-m_n \rbrace$ every of which must be replicated on multiple WPs to make them arbitrary fault tolerant.
-Each map task $m_i$ is assigned to a different WPG $g_i \in \lbrace g_1, g_2, ...
+Formally, let $i = 1,2,3...n$, where $n \in \mathbb{Z}_+$.
+LPP splits the input text file $S$ in $n$ parts $\lbrace s_1, s_2, ...
+s_n \rbrace$ called \textit{splits}; each split $s_i$ is associated to an AFT-Map Task $m_i \in \lbrace m_1, m_2, ...
+m_n \rbrace$.
+Each AFT-Map Task $m_i$ is assigned to WPG $g_i \in \lbrace g_1, g_2, ...
 g_n \rbrace$.
-As we will explain later, LPP, checking received outputs from each group, we can achieve arbitrary fault tolerance for every scheduled task.
-Obliviously to tolerate at most $f$ arbitrary failures of each task, each WPG must contains at least $2f+1$ different processes.
-Then our design requires at least $n(2f+1)$ different WPs.
+Then $2f+1$ different WPs belonging to WPG $g_i$ perform the same map task replica.
+LPP, checking received outputs from each WP of each group, picks the most voted results which is expected correct if no more than $f$ arbitrary faults occur.
+Obviously Reduce-Phase is performed in similar ways.
 
-This design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs.
-If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG, increasing the number PP backups too.
+Clearly, this design require more resources respect to classic MapReduce scheme: to tolerate at most $f$ arbitrary failures, each WPG have to contains at least $2f+1$ different WPs, therefore a total of $n(2f+1)$ different WPs are required (to which is also added a certain number of PPs run on different machine).
+
+Although its very high costs, this design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs.
+If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG (increasing the number of PP backups too).
 
@@
 
-Given the system model described previously, a solution to tolerate at most $f$ arbitrary faults during each task would be the following: current LPP assigns a given map/reduce task to a WPG contacting its $2f + 1$ WPs; then, after retrieving the outputs from replicas, picks the most voted results which is expected correct if no more than $f$ arbitrary faults occur.
+At this point high costs of this solution should be clear to reader because everything is replicated $2f + 1$ times as map/reduce task, data transmissions and so on.
+Can we have a good level of fault tolerance without worsening performance?
+How can we do AFT-Map Task and AFT-Reduce Task efficiently?
 
-This simplistic solution is very expensive because it replicates everything $2f + 1$ times: task execution, communication of map task outputs and so on.
-We use a set of techniques to avoid these costs and do things efficiently:
+In this section we will explain a set of solutions and techniques which we have adopt in our system to reduce costs and do things efficiently:
 
-\subsection{Digest outputs} As explained above, in order to consider a map/reduce task correct, tolerating at most $f$ faulty processes, $f + 1$ matching outputs, coming from at least $2f + 1$ WPs belonging to a given WPG,  have to be received.
+\subsection{Digest outputs} As explained above, in order to consider any AFT-Map Task/AFT-Reduce Task correct, tolerating at most $f$ faulty processes, $f + 1$ matching outputs, coming from at least $2f + 1$ WPs belonging to a given WPG to which we have assign the aforementioned task, have to be received.
 
-To validate task's output, since outputs computed by worker processes can be very large, in order to avoid pointless additional network traffic, we have adopted an approach according to which LPP fetches and compares \textit{digests}, a bit string of a fixed size obtained using a hash function.
-The main advantage of this technique is that, digest size are many times smaller than task's data output, allowing us to reduce network traffic among servers, increasing system's performance.
+Since outputs computed by WPs can be very large, we have adopted an approach according to which, instead of to compare raw data, LPP fetches and compares \textit{digests} that is fixed size strings obtained from WPs outputs using an hash function.
+The main advantage of this technique is that digest size are many times smaller than task's data output, allowing us to validate task's output reducing network traffic among servers.
 
-\subsection{Locality-Aware Deferred Execution}
+\subsection{Locality-And-State-Aware Deferred Execution}
 
-Waiting for $2f + 1$ matching replies during a AFT Map-Task can be a waste of time especially when no faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ Map-Task for each AFT Map-Task.
+Waiting for $2f + 1$ matching replies during any AFT Map-Task/AFT-Reduce Task can be a waste of time especially when no faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ replicas for a given AFT-Map Task/AFT-Reduce Task.
 
-Therefore, to minimize both the number of Map-Task executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware Deferred Execution}.
+Therefore, to minimize both the number of replicas executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware Deferred Execution}.
 
-According to that solution, during a AFT Map-Task execution, only $f + 1$ Map-Task replicas are started checking if they all return the same result.
-If a time-out elapses or some return results do not match, more Map-Task replicas (up to $f$) are started, until we obtain $f + 1$ matching replies.
+According to that solution, during a AFT Map-Task/AFT-Reduce Task execution, only $f + 1$ replicas are started checking if they all return the same result.
+If a time-out elapses or some return results do not match, more replicas (up to $f$) are started, until we obtain $f + 1$ matching replies.
 When faults are unlikely, this approach, which we believe to be energy-saver\footnote{Assuming that idle WPs consume less energy respect to non-idle WPs, minimize the number of Map-Task executed involves minimize the amount of electricity used.}, is capable to minimize the number of WPs involved into computations respect to basic scheme, improving overall system performance.
 
-Moreover, this mechanism can reduce overall system response time because it is designed to minimize data transfer time too.
-When an AFT Map-Task starts $f + 1$ Map-Task replica on WPs, the latter are not chosen at random but according to their network location; in fact, Map-Task are scheduled firstly to the $f + 1$ nearest nodes giving priority to them.
+Moreover, this mechanism can reduce overall system response time because it is designed to minimize data transfer time too because our scheduler gives priority to \textit{nearest} WPs.
+When an AFT-Map Task/AFT-Reduce Task starts $f + 1$ replica on WPs, the latter are not chosen at random but according to their network location; in fact, the tasks are scheduled firstly to the $f + 1$ nearest nodes.
 Only when we can't get $f + 1$ matching replies, the most distant nodes are used.
@@
 
+We have designed our task scheduler to be also \textit{state-aware} since priority is given to those WPs whit minimum CPU utilization which we compute using \texttt{mpstat} tool.
+WP's state is acquired indirectly by LPP through their replies.
+
 \subsection{Speculative Execution}
 
-Although the advantages of the locality-aware deferred execution mechanism, we believe that waiting for $f + 1$ matching Map-Task for every AFT Map-Task results before starting the Reduce-Phase can worsen the time for the job completion, especially when WPs arbitrary failures are uncommon.
-Formally, assuming that we have $n$ WPG, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies; all Map-Phase may require long time especially when network traffic or data set size are huge.
+Although the advantages of the deferred execution mechanism describes above, we believe that waiting for $f + 1$ matching digest for all AFT Map-Tasks before starting the Reduce-Phase can worsen the time for the job completion, especially when WPs arbitrary failures are uncommon.
+Remember that, assuming that we have $n$ WPGs, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies; all Map-Phase may require long time due, for instance, to network traffic or big  data-set.
 
-A way to increase system's performance reducing its response time is the following: when all scheduled AFT Map-Tasks have received the \textit{first} Map-Task result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finish.
+A way to increase system's performance reducing its response time is the following: when all $n$ scheduled AFT Map-Tasks have received the \textit{first} replica's result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finish.
 Essentially, our system make a bet according to which arbitrary faults are highly unlikely therefore first Map-Task replies are considered as correct.
-This mechanism is called \textit{Speculative Execution}.
+This mechanism is known in literature called \textit{Speculative Execution}, an optimization technique applied frequently in computer technology.
 
 Obviously validate the correctness of first Map-Task replies is critical otherwise job's output can be incorrect.
-In order to do that, all AFT Map-Tasks keep on waiting their $f + 1$ matching replies even when Reduce-Phase is started.
+To do that, all scheduled AFT Map-Tasks keep on waiting their $f + 1$ matching replies even when Reduce-Phase is started.
 When Map-Phase is fully finish, if is detected that the input used in the Reduce-Phase was not correct, Reduce-Phase will be restarted with the correct input, otherwise we can finish our job in much less time.
@@
 
-\subsection{Data Locality-Aware Reduce Scheduling}
+\subsection{Data-Locality-Aware Reduce Scheduling and Shuffle}
 
-Since in order to achieve fault tolerance we have replicate all task $2f + 1$ times, data transfers among servers are replicated too, generating an huge amount of network traffic.
+So far we have not yet mentioned the shuffle task according to which WP redistribute data (produced by the map function), such that all data belonging to one key is located on the same WP's node.
+Unlike Hadoop implementation, shuffle task is difficult and expensive due to process replication and to optimization technique described so far.
+Clearly, due to process replication, data transfers among servers are replicated too, generating an huge amount of network traffic.
 Evidently, when large data set are involved, move data repeatedly among server became a bottleneck.
 
-Therefore we have adopted a design aware of data locations and sizes capable to reduce the overall amount of transferred data; that solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}"; in other words  "\textit{moving computation towards data is cheaper than moving data towards computation}".
+Therefore we have adopted a design aware of data locations capable to reduce the overall amount of transferred data: this approach is called \textit{Data-Locality-Aware Reduce Scheduling}.
+That solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}"; in other words  "\textit{moving computation towards data is cheaper than moving data towards computation}".
 
-To be more precise, when a WP complete a map task, it send as output to LPP two very important information: a string containing data output digest and a value representing output data size.
-According to Hadoop terminology, map task output are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one?
+Using the same Hadoop terminology, map task output, produces by every WPs, are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one?
+Then, why not schedule a AFT-Reduce Task to the WPG which nodes has bigger partition?
+In this way we can avoid transferring huge amount of data increasing overall system performances.
 
-Assume for simplicity that no faults occurs and to have only two WPGs $\lbrace g_1, g_2 \rbrace$.
+To explain how our scheduler works, let's illustrate an example: assume for simplicity to have only two WPGs $\lbrace g_1, g_2 \rbrace$.
 Let $P_{i:g_i}$ the partition owned by WPG $g_i$ which contains all key-value pairs which must be submitted to reduce task $R_i$.
-The problem is how to perform a locality-aware reduce task scheduling; in other word, which WPG $g_i$ have to run reduce task $R_i$ reducing shuffled data?
-
 Suppose that $P_{1:g_1}$, $P_{2:g_1}$, $P_{1:g_2}$ and $P_{2:g_2}$ have a size of 300 MB, 150 MB, 150 MB and 300 MB respectively.
-Clearly, scheduling $R_1$ at $g_1$ and $R_2$ at $g_2$ reduce the amount of transferred data among WPGs by 50\%.
-Obliviously using this approach is possible to perform a locality-aware shuffle task capable to reduce network traffic, applying locality to reduce task scheduling.
+In this context LPP schedules $R_1$ to $g_1$ and $R_2$ to $g_2$ because in this way is able to reduce transferred data among WPGs by 50\%.
+In other words, LPP is design to schedule AFT-Reduce Tasks reducing overall amount of shuffled data.
 

### 2019-09-20 Paper.tex
dsadsadas

@@
 
-Another difference Hadoop \textit{JobTracker} process regards task scheduling approach.
+Another very important aspect of PP is its ability to recognize duplicated requests coming from client; adopting a \textit{most-once semantics}, LPP is able to recognize duplicates re-forwarding its reply to client while client process, if it detects that LPP is been crashed, it will forward a query to Zookeeper cluster in order to know who is the new LPP.
+Note that WP too are designed according to most-once semantics.
+
+Another difference with Hadoop \textit{JobTracker} process regards task scheduling approach.
 In our design LPP schedules tasks to WP using a \textit{push-based} approach, contrariwise Hadoop JobTracker schedules task using a \textit{pull-based} approach where WP ask for tasks\cite{LARTS}.
@@
 
-\section{System features}
+\section{System's features}
 
@@
 \subsection{Crash failure detection} To guarantee the correct functioning of the system, is critical to be able to detect WP and PP crash failure.
-To resolve this problem we have exploited some features of Apache Zookeeper.
 
@@
 When session expiration occurs, Zookeeper cluster will delete all ephemeral nodes owned by that session and immediately notify all connected clients of the change.
-
 When any client establishes a session with a Zookeeper cluster, a time-out value is used by the cluster to determine when the client's session expires.
@@
 
-Therefore using that feature, we adopted a very simple design according to which any process must to "sign up" creating his own ephemeral node in Zookeeper Cluster in known paths (note that znode paths of PPs and WPs are different in order to not interfere with leader election of PPs).
+Therefore we have exploit this Zookeeper feature design our system in such a way any system's process, except for client process, must to "sign up" creating his own ephemeral node in Zookeeper Cluster before to start to perform its task \footnote{To be precise that ephemeral znodes corresponding to PPs and WPs are stored in different path to not interfere with leader election algorithms}.
+To be more precise, every WPs, whose ID is \texttt{i} and belonging to WPG \texttt{g}, creates a znode named \texttt{/membership/i\_g}.
+Then, when any WP crashes, LPP, which watch for changes upon \texttt{/membership} znode path, is notified by Zookeeper
 
-It will be the responsibility of LPP to watch for WP's ephemeral node deletions; this approach makes WP status checking very simple.
-System coordination and membership is facilitated too, since any ephemeral node is used to store information about process that created (ID, Group ID etc.).
+\subsection{Election algorithm}
 
-\subsection{Primary process leader election algorithm}
+As we said previously, our system is based on multiple PP backup copies which run independently on different machines.
+Since we need a leader, let's now describe in details how we have managed leader election problem which we have resolved, once again, using Apache Zookeeper.
+
+Suppose that \texttt{ROOT} is a valid path of an existing znode.
+To apply as possible leader, any PP creates a znode child into \texttt{ROOT} using \texttt{SEQUENCE} and \texttt{EPHEMERAL} flags.
+When \texttt{SEQUENCE} is used, ZooKeeper cluster automatically appends a sequence number to the new znode that is greater than any one previously appended to a child of \texttt{ROOT}.
+The PP, which created the znode with the smallest appended sequence number, become leader.
+
+Obliviously is important to watch for failures of the leader in a such way that a new PP arises as the new leader when leader fails.
+Note that, since we have used \texttt{EPHEMERAL} flag during znode creation, when leader fails the smallest znode will be deleted by Zookeeper cluster.
+if we make sure that all PPs watch for the next znode down on the sequence of znodes, if a PP receives a notification that the znode it is watching is gone, then it becomes the new leader since there is no smaller znode.
+
+A complete description of leader election algorithm is shown in Algorithm \ref{alg:leaderElection}.
 
@@
 
-Let's now describe in details how we have resolved leader election problem of a PP using Apache Zookeeper.
+\section{System's work-flow}
 
-Suppose that \texttt{ROOT} is a valid path of an existing znode.
-To apply as possible leader, any PP creates a znode child into \texttt{ROOT} using \texttt{SEQUENCE} and \texttt{EPHEMERAL} flags.
-When \texttt{SEQUENCE} is used, ZooKeeper cluster automatically appends a sequence number to the new znode that is greater than any one previously appended to a child of \texttt{ROOT}.
-The PP, which created the znode with the smallest appended sequence number, become leader.
-
-Obliviously is important to watch for failures of the leader in a such way that a new PP arises as the new leader when leader fails.
-Note that, since we have used \texttt{EPHEMERAL} flag during znode creation, when leader fails the smallest znode will be deleted by Zookeeper cluster.
-if we make sure that all PPs watch for the next znode down on the sequence of znodes, if a PP receives a notification that the znode it is watching is gone, then it becomes the new leader since there is no smaller znode.
-
-A complete description of leader election algorithm is shown in Algorithm \ref{alg:leaderElection} while our implementation is in \texttt{SDCC-Project/aftmapreduce/cloud/zookeeper}
-
-\section{The algorithm}
-
-In this section we will provide a detailed description of our MapReduce algorithm used to fully accomplish any client's word-count request.
-Our algorithm is made up of five phases every of which have to be successfully completed in order to complete a request.
+To In this last section we will sum up how our system works in several steps to better understand some aspect of our solution.
 
@@
 
-The first phase of our algorithm expects that client would upload their test input file into a DFS (\textit{Distributed File System)} or, equivalently, into an external storage service.
+In the first place, any client uploads its test input file into Amazon S3 using its digest, obtained making use of SHA-512 hash algorithm, as key.
+Remember that clients, to perform upload operation, have to require a pre-signed URL to LPP, which network location will be obtained querying Zookeeper cluster.
 
@@
 
-After data upload, client sends a word-count request to current LPP.
+When data upload is complete, client sends a word-count request to current LPP which execute several initialization operations in order to register incoming request.
+To be more precise, LPP creates two new znodes into Apache Zookeeper cluster: one of them is used to store request related information (request's status information, text input data digest etc.) necessary to restore LPP state in case of crash; the other is used instead to store the digest of job's output.
 
-When that request is been received, LPP, after to have written into Zookeeper cluster all necessary information  in order restore its state after a crash failure (request's status information, text input data digest etc.),  notifies client that his request is been accepted by system, starting Map phase.
+If all these znodes are successfully created, received request is considered as "accepted" and clients start to wait for change the output's znode while LPP can start Map-Phase.
+If any error occurs during this phase, client have to re-forward its request to LPP until it will receive acceptance confirmation; re-forwarding requests is fully safe since LPP can filter duplicated requests.
+If LPP crashes, clients will wait for a new leader before to re-forwarding its request.
 
-When LPP response is been received, client starts to wait for a new notification by Zookeeper cluster (watching a specified znode) which will signalize computation completion.
+\subsection{Map-Phase}
 
-If any error occurs during this phase, client have to re-forward its request to LPP until it will receive acceptance confirmation.
+During this phase, LPP fetches input text file from Amazon S3 using the key provided by client; then, it splits it into $n$ parts where $n$ is the number of WPGs currently registered on Zookeeper cluster.
+Afterwards LPP schedules $n$ AFT-Map Tasks assigning them to each WPG.
+Fault tolerance mechanism is been already described previously but note that our prototype is designed to check at runtime the number of currently available WPs into a WPG calculating automatically reachable fault tolerance level (for example if there are three WP currently on-line of a specified group, the system behaves properly in order to tolerate one arbitrary failure).
 
-Note that our system is able to manage duplicated requests because we have adopted a \textit{most-once semantics}; in fact, LPP is able to recognize duplicates re-forwarding its reply to client while client, if it detects that LPP is been crashed, forwards a query to Zookeeper cluster in order to know who is the new LPP.
+Normally, when all AFT-Map Tasks finish successfully, LPP performs a checkpoint of request's state writing into Zookeeper cluster all data required to recover from a LPP crash (these data include digest outputs from all WPGs and information about owned partitions size).
+Since we have adopt speculative execution mechanism, Reduce-Phase will be stared immediately after one replica replies of all AFT Map-Tasks; in this case there is no point on doing a checkpoint because we cannot trust on Map-Phase output used.
+Therefore, we will make the Map-Phase checkpoint only if speculative execution fails.
 
-\subsection{Map phase}
+Note that if LPP crashes, the new leader is able to recover all pending requests from last checkpoint restarting them.
 
-LPP splits received text into $n$ splits where $n$ is the number of WPGs currently available in the cluster (this number is checked at runtime).
-Then LPP starts \textit{Map Phase} during which $n$ \textit{Arbitrary-Fault-Tolerant Map Tasks} (AFT-MTs) are initialized and assigned to every WPGs (note that each WPG manages a different AFT-MT).
+\subsection{Shuffle and Reduce Phase}
 
-To make this phase fault tolerant, each AFT-MT is replicated using the WPs available into a WPG specified by LPP.
-As explain in previous sections deferred execution and digest outputs are used.
-Our prototype is designed to check at runtime the number of currently available WPs into a WPG calculating automatically fault tolerance level (for example if there are three WP currently on-line of a specified group, the system behaves properly in order to tolerate one arbitrary failure).
-
-When all AFT-MTs finish successfully, LPP perform a checkpoint storing into Zookeeper cluster a set of meta-data used to restore LPP status in case of crash (these data include digest outputs from WPGs and some information about computed data outputs owned by WPGs).
-
-In case of LPP crash (note that also an high amount of arbitrary fails of WPs determines a LPP crash), after using our leader election algorithm, a PP backup copy becomes leader.
-Then the new leader recovers previous leader's status from last checkpoint querying Zookeeper cluster.
-All pending requests are restarted according to last checkpoint while input text data are retrieved, if necessary, from DFS or an equivalent storage service.
-
-\subsection{Locality-aware shuffle and reduce phase}
-
-Any mapper send to LPP information about computed data like its size.
-Using all informations collected from each on-line WP during previous phase, LPP perform a locality-aware data shuffle according to which our system avoids transferring large partitions, shuffling smaller ones and saving network bandwidth.
-
-Since, according to our design, any WPG can receive a partition from any other, we need to wait until all mappers complete to certainly designate all the network locations of partitions.
-When map phase is fully done and all the network locations known, LPP starts to coordinates shuffle phase, ordering to some or all WGs to move part of their data to precisely location.
-These location are computed in order to shuffle smaller partition only.
-
-When shuffle phase is fully complete, LPP starts to coordinate $n$ Arbitrary-Fault-Tolerant Reduce Tasks (AFT-RTs) assigning them to every WPGs which now have all necessary data to perform this kind of operation.
-When all AFT-RTs fully finish, LPP perform another checkpoint in order to restore from an eventual LLP's crash.
-
-If too many arbitrary errors occur, making AFT-RTs completion impossible, it's enough to restart current phase.
+We have already described how we have manage Shuffle and Reduce Phase and, anyhow, there are no relevant concepts to be explored.
+Just note that another request status checkpoint will be made after the end of Reduce Phase.
+If too many arbitrary errors occur, it's enough to restart current phase.
 
@@
 
-When reducer phase is fully done, LPP start to retrieve all reduce outputs from WPs.
-To be more precise, for every available WPG in system LPP picks a single WP which, according to data received during last phase, has computed correct outputs.
-
-Then all reduce outputs are finally concatenated in an single output file.
-LPP stores output file into Amazon S3 using its digest as key.
-Then LPP informs the client sending output file digest through which client can retrieve his output.
+When reducer phase is fully done, LPP starts to retrieve all AFT-Reduce TASK outputs from each WPG sending a specific request to the nearest and least loaded WP belonging to them.
+When all outputs are finally retrieved and concatenated in an single output file, LPP stores output file into Amazon S3 using output file digest as key which will be written into Zookeeper cluster.
+Client process, informed of the completion of his request, can fetch the output's digest from Zookeeper cluster and use it to download output.
 

### 2019-09-26 Paper.tex
dasddas

@@
 In this paper we present a MapReduce runtime system as a solution to these problems.
-Although job's execution using our system requires more resources respect to other implementations due to process replications, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
+Although job's execution using our system requires more resources respect to other implementations due to process replication, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
 \end{abstract}
 
-\keywords{MapReduce, Arbitrary Fault Tolerance, Locality Awareness, Speculative Execution, Leader Election Algorithm, Deferred Execution}
+\keywords{MapReduce, Arbitrary Fault Tolerance, Data-Locality Awareness, Speculative Execution, Leader Election Algorithm, Deferred Execution}
 \maketitle
@@
 
-In order to enable communication with the Internet and therefore allow a local computer to connect to our system, we have adopt AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} which able us to associate to some of our EC2 instance to a public static IPv4 addresses\footnote{Public IPv4 addresses associated to any EC2 instances by default change after every start.
-Therefore, if an Amazon EC2 crashed and have to be restarted, client wouldn't able to connect to it due to address change.}.
+In order to enable communication with the Internet and therefore allow a local computer to connect to our system, we have adopt AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} which able us to associate to some of our EC2 instance to a public static IPv4 addresses.
 
-Observe that processes are not all the same but several kind of these exist, with its own features and aims: although we will describe them in detail in following section, just note that we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);
+Observe that processes are not all the same but several kind of these exist, with its own features and aims: although we will describe them in detail in following section, just note that we distinguish three process types: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);
 
-Note that our MapReduce system is been implemented to execute word-count job only.
-We have built our system from scratch using Go programming language\footnote{\url{https://golang.org}} using some external libraries, which are all reported in table \ref{tab:libraries}.
+Note that our MapReduce system, capable to execute word-count job only, is been implemented from scratch using Go programming language\footnote{\url{https://golang.org}} using some external libraries, which are all reported in table \ref{tab:libraries}.
 
@@
 
-It can interact with system's key-value storage service (i.e.
+It can interact with a key-value storage service (i.e.
 DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading.
@@
 
-However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}.
+However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that PP, and the host where it is running, may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}.
 Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by.
@@
 
-Therefore we have adopt a design according to which LPP save its state regularly.
+Therefore we have adopt a design according to which LPP saves its state regularly.
 Since LPP state consists on a very small amount of data, we have design LPP to store its state into Apache Zookeeper cluster upon the occurrence of certain events.
@@
 
-Another very important aspect of PP is its ability to recognize duplicated requests coming from client; adopting a \textit{most-once semantics}, LPP is able to recognize duplicates re-forwarding its reply to client while client process, if it detects that LPP is been crashed, it will forward a query to Zookeeper cluster in order to know who is the new LPP.
+Another very important aspect of PP is its ability to recognize duplicated requests coming from client (which can retransmitt a same request) re-forwarding responses; in other words, we have adopt a \textit{most-once semantics}.
 Note that WP too are designed according to most-once semantics.
@@
 Another difference with Hadoop \textit{JobTracker} process regards task scheduling approach.
-In our design LPP schedules tasks to WP using a \textit{push-based} approach, contrariwise Hadoop JobTracker schedules task using a \textit{pull-based} approach where WP ask for tasks\cite{LARTS}.
+In our design LPP schedules tasks to WP using a \textit{push-based} approach, contrariwise Hadoop JobTracker schedules task using a \textit{pull-based} approach where WPs ask for tasks\cite{LARTS}.
 
@@
 To achieve fault tolerance we have adopt a design according to which each task is executed more than once by different processes running on different host.
-To do this, as you can see from figure \ref{fig:model}, we have adopt a design according to which all worker processes are organized in several groups which we have used to mask one or more faulty processes: these groups are called \textit{Worker Processes Group} (WPG).
-To be more precise, an WPG is a set of identical WP, each of which execute \textit{the same commands using the same input data in the same order}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.
+To do this, as you can see from figure \ref{fig:model}, all worker processes has been organized in several groups which we have used to mask one or more faulty processes: these groups are called \textit{Worker Processes Group} (WPG).
+To be more precise, an WPG is a set of identical WP, each of which execute \textit{the same commands using the same input data}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.
 
@@
 
-Clearly, this design require more resources respect to classic MapReduce scheme: to tolerate at most $f$ arbitrary failures, each WPG have to contains at least $2f+1$ different WPs, therefore a total of $n(2f+1)$ different WPs are required (to which is also added a certain number of PPs run on different machine).
+Clearly, this design requires more resources respect to classic MapReduce scheme: to tolerate at most $f$ arbitrary failures all WPGs have to contain at least $2f+1$ different WPs, therefore a total of $n(2f+1)$ different WPs is required.
 
 Although its very high costs, this design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs.
-If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG (increasing the number of PP backups too).
+If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG.
 
@@
 
-At this point high costs of this solution should be clear to reader because everything is replicated $2f + 1$ times as map/reduce task, data transmissions and so on.
+At this point should be clear to reader that our design, despite its simplicity, is very expensive because almost everything is replicated $2f + 1$ times like map/reduce tasks, data transmissions and so on.
 Can we have a good level of fault tolerance without worsening performance?
@@
 
-In this section we will explain a set of solutions and techniques which we have adopt in our system to reduce costs and do things efficiently:
+In this section we will explain a set of solutions and techniques which we have adopt in our system to optimize it reducing costs and doing things efficiently.
 
@@
 
-Since outputs computed by WPs can be very large, we have adopted an approach according to which, instead of to compare raw data, LPP fetches and compares \textit{digests} that is fixed size strings obtained from WPs outputs using an hash function.
+Since outputs computed by WPs can be very large, we have adopted an approach according to which, instead of to compare raw data, LPP fetches and compares \textit{digests}, that is fixed size strings obtained from raw data outputs using an hash function.
 The main advantage of this technique is that digest size are many times smaller than task's data output, allowing us to validate task's output reducing network traffic among servers.
@@
 
-Waiting for $2f + 1$ matching replies during any AFT Map-Task/AFT-Reduce Task can be a waste of time especially when no faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ replicas for a given AFT-Map Task/AFT-Reduce Task.
+It is frequently a good idea to distinguish between the most common case and the worst possible case and treat them differently.
+In our system the occurrence of $f$ arbitrary faults represents the worst possible case, not the common in which less than $f$ errors occur.
+To improve considerably system's performance is important to make the common case fast.
+When worst case occurs, is sufficient to make it correct.
 
-Therefore, to minimize both the number of replicas executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware Deferred Execution}.
+Therefore waiting for $2f + 1$ matching replies during any AFT-Map Task/AFT-Reduce Task can be a waste of time especially when fewer faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ replicas for a given AFT-Map Task/AFT-Reduce Task.
+
+Therefore, to minimize both the number of replicas executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware-And-State Deferred Execution}.
 
@@
 
-We have designed our task scheduler to be also \textit{state-aware} since priority is given to those WPs whit minimum CPU utilization which we compute using \texttt{mpstat} tool.
-WP's state is acquired indirectly by LPP through their replies.
+We have designed our task scheduler to be also \textit{state-aware} since priority is given to those WPs which have minimum CPU utilization which we compute using \texttt{mpstat} tool.
+WPs states are acquired indirectly by LPP through their replies.
 
@@
 
-Although the advantages of the deferred execution mechanism describes above, we believe that waiting for $f + 1$ matching digest for all AFT Map-Tasks before starting the Reduce-Phase can worsen the time for the job completion, especially when WPs arbitrary failures are uncommon.
-Remember that, assuming that we have $n$ WPGs, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies; all Map-Phase may require long time due, for instance, to network traffic or big  data-set.
+Although the advantages of the deferred execution mechanism describes above, we believe that waiting for $f + 1$ matching digest for all AFT Map-Tasks before starting the Reduce-Phase can worsen the time for the job completion in some situations.
+Assuming that we have $n$ WPGs, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies to fully complete Map-Phase, which may require long time.
 
-A way to increase system's performance reducing its response time is the following: when all $n$ scheduled AFT Map-Tasks have received the \textit{first} replica's result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finish.
-Essentially, our system make a bet according to which arbitrary faults are highly unlikely therefore first Map-Task replies are considered as correct.
-This mechanism is known in literature called \textit{Speculative Execution}, an optimization technique applied frequently in computer technology.
+A way to increase system's performance reducing its response time is the following: when all $n$ scheduled AFT Map-Tasks have received the \textit{first} replica's result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finishes.
+Essentially, our system make a bet according to which arbitrary faults are highly unlikely and therefore first Map-Task replies can be considered as correct.
+This mechanism is known in literature \textit{Speculative Execution}, an optimization technique applied frequently in computer technology.
 
@@
 So far we have not yet mentioned the shuffle task according to which WP redistribute data (produced by the map function), such that all data belonging to one key is located on the same WP's node.
-Unlike Hadoop implementation, shuffle task is difficult and expensive due to process replication and to optimization technique described so far.
-Clearly, due to process replication, data transfers among servers are replicated too, generating an huge amount of network traffic.
-Evidently, when large data set are involved, move data repeatedly among server became a bottleneck.
+Unlike Hadoop implementation, shuffle task is difficult and expensive due to processes replication.
+Clearly data transfers among servers have to be replicated, generating an huge amount of network traffic and evidently, when large data set are involved, move data repeatedly among server became a bottleneck.
 
 Therefore we have adopted a design aware of data locations capable to reduce the overall amount of transferred data: this approach is called \textit{Data-Locality-Aware Reduce Scheduling}.
-That solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}"; in other words  "\textit{moving computation towards data is cheaper than moving data towards computation}".
+That solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}".
 
 Using the same Hadoop terminology, map task output, produces by every WPs, are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one?
-Then, why not schedule a AFT-Reduce Task to the WPG which nodes has bigger partition?
+Then, why not schedule an AFT-Reduce Task to the WPG which nodes has bigger partition?
 In this way we can avoid transferring huge amount of data increasing overall system performances.
 
-To explain how our scheduler works, let's illustrate an example: assume for simplicity to have only two WPGs $\lbrace g_1, g_2 \rbrace$.
+To explain how our scheduler works, let's illustrate it with an example: assume for simplicity to have only two WPGs $\lbrace g_1, g_2 \rbrace$.
 Let $P_{i:g_i}$ the partition owned by WPG $g_i$ which contains all key-value pairs which must be submitted to reduce task $R_i$.
@@
 In this context LPP schedules $R_1$ to $g_1$ and $R_2$ to $g_2$ because in this way is able to reduce transferred data among WPGs by 50\%.
-In other words, LPP is design to schedule AFT-Reduce Tasks reducing overall amount of shuffled data.
 

### 2019-09-30 Paper.tex
Andrea

@@
 
-\title{Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce}
+\title{Arbitrary Fault-Tolerant and Locality-Aware MapReduce}
 
@@
 
-Another very important aspect of PP is its ability to recognize duplicated requests coming from client (which can retransmitt a same request) re-forwarding responses; in other words, we have adopt a \textit{most-once semantics}.
+Another very important aspect of PP is its ability to recognize duplicated requests coming from client (which can re-transmit a same request) re-forwarding responses; in other words, we have adopt a \textit{most-once semantics}.
 Note that WP too are designed according to most-once semantics.
@@
 If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG.
+te
 

### 2019-10-02 Slide/Slide.tex
add slides

\documentclass[10pt]{beamer}
%\usetheme[
%%% option passed to the outer theme
%    progressstyle=fixedCircCnt,   % fixedCircCnt, movingCircCnt (moving is deault)
%]{}

% If you want to change the colors of the various elements in the theme, edit and uncomment the following lines

% Change the bar colors:
%\setbeamercolor{Feather}{fg=red!20,bg=red}

% Change the color of the structural elements:
%\setbeamercolor{structure}{fg=red}

% Change the frame title text color:
%\setbeamercolor{frametitle}{fg=blue}

% Change the normal text color background:
%\setbeamercolor{normal text}{fg=black,bg=gray!10}

%-------------------------------------------------------
% INCLUDE PACKAGES
%-------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}

%-------------------------------------------------------
% DEFFINING AND REDEFINING COMMANDS
%-------------------------------------------------------

\usetheme{Frankfurt}

%-------------------------------------------------------
% INFORMATION IN THE TITLE PAGE
%-------------------------------------------------------

\title[] % [] is optional - is placed on the bottom of the sidebar on every slide
{ % is placed on the title page
      \textbf{Arbitrary Fault-Tolerant and Locality-Aware MapReduce}
}

\subtitle[]
{
      \textbf{Sistemi Distribuiti e Cloud Computing 2018-2019}
}

\author[Andrea Graziani - 0273395]
{      Andrea Graziani - 0273395 \\
      {}
}

\institute[]
{
      Università degli Studi di Roma “Tor Vergata” \\
      FACOLTA' DI INGEGNERIA \\
      Corso di Laurea Magistrale in Ingegneria Informatica

  %there must be an empty line above this line - otherwise some unwanted space is added between the university and the country (I do not know why;( )
}

\date{\today}

%-------------------------------------------------------
% THE BODY OF THE PRESENTATION
%-------------------------------------------------------

\begin{document}

%-------------------------------------------------------
% THE TITLEPAGE
%-------------------------------------------------------

{% % this is the name of the PDF file for the background
\begin{frame}[plain,noframenumbering] % the plain option removes the header from the title page, noframenumbering removes the numbering of this frame only
  \titlepage % call the title page information from above
\end{frame}}

\section{System Architecture}

\begin{frame}[fragile]{System Architecture}{}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{./images/Architecture.png}
  \caption{System Architecture}
\end{figure}
\end{frame}

% ************************************************************************** %

\subsection{System's processes}

\begin{frame}{System Architecture}{}

\begin{itemize}

\item What assumptions we have made?

\item We distinguish three process types: 
\vspace{10pt}
\begin{itemize}
\item \textit{Client Process}
\item \textit{Primary Process} (PP) 
\item \textit{Worker Process} (WP)
\end{itemize}
\vspace{10pt}

\item How we made the system fault tolerant? What kind of fault tolerance can be achieved with this design?
\item What kind of semantics do we have adopted?
\item Is our system scalable?
\item Our system can be elastic? \textbf{Yes... but}
\item What are the advantages/disadvantages of our solution?
\end{itemize}
\end{frame}

% ************************************************************************** %
\section{System features}

\subsection{Locality-And-State-Aware Deferred Execution}

\begin{frame}{System features}{Deferred Execution}

\begin{itemize}
\item By default our system is design to use the \textit{Deferred Execution} approach during task scheduling.

\vspace{10pt}
\begin{itemize}
\item What's meant by deferred execution and how it works?

\item What are the advantages of this approach? And the disadvantages?

\item What happens if LPP/WPs crashes?

\item Why \textit{Locality-Aware}?

\item Why \textit{State-Aware}?
\end{itemize}
\vspace{10pt}
\end{itemize}
\end{frame}

\subsection{Speculative Execution}

% ************************************************************************** %
\begin{frame}{System features}{Speculative Execution}

\begin{itemize}

\item In order to improve system's performance we have adopt an approach based on the so called \textit{Speculative Execution}
\vspace{10pt}
\begin{itemize}
\item What's meant by speculative execution? How it works?

\item What happens if the input used during Reduce-Phase is detected as incorrect?

\item What happens if LPP/WPs crashes?
\end{itemize}
\vspace{10pt}
\item Can we do better? \textbf{Yes...but...}
\end{itemize}

\end{frame}

\subsection{Data-Locality-Aware Reduce Scheduling and Shuffle}

% ************************************************************************** %
\begin{frame}{System features}{Data-Locality-Aware Reduce Scheduling and Shuffle}

\begin{itemize}

\item Our system is designed to schedule reduce task considering data locality in order to reduce the overall amount of transferred data between WPs: this approach is called \textit{Data-Locality-Aware Reduce Scheduling}.
\vspace{10pt}
\begin{itemize}

\item "\textit{Moving computation towards data is cheaper than moving data towards computation}".
\item How it works?

\end{itemize}

\end{itemize}

\end{frame}

\subsection{Other features}

% ************************************************************************** %
\begin{frame}{System features}{Other features}

\begin{itemize}
\item Digest output.
\item Leader election and crash failure detection based on Apache Zookeeper.
\end{itemize}

\end{frame}

\begin{frame}[plain,noframenumbering]
  Grazie per l'attenzione!
\end{frame}

\end{document}
